### 2020-08-20 draft.Rmd
Updated results

---
title: "A Global Market for Marine Conservation"
subtitle: "Draft"
author:
  - "Juan Carlos Villaseñor-Derbez"
  - "Darcy Bradley"
  - "Christopher Costello"
  - "Juan Mayorga"
  - "Andrew Plantinga"
date: "Prepared on `r format(Sys.time(), '%B %d, %Y')`"
abstract: "Humanity depends on the ocean for livelihood, subsitance, and way of life. Yet, many of our activities continiously pose a threat to marine populations and ecosystems. The implementation of Marine Protected Areas (MPAs), where extractive activities are regulated or prohibited on the basis of spatial deliniations, are one of many ways to manage the oceans. Current intenrational agreements call to achieve a certain amount of within-country conservation. Here we explore the benefits from implementing a market for conservation in which nations trade conservation towards a global target. We find that such a market reduces the costs of conservation by 46%, relative to a BAU scenario without a market where each country protects a fixed portion of their waters. When creating 12 distinct markets based on biogeography regionalization, we find that costs are reduced by 34.8%."
fontsize: 12pt
output:
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: no
header-includes:
  - \usepackage{multirow}
  - \usepackage{float}
  - \usepackage{pdfpages}
  - \usepackage{placeins}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.pos = "!H",
                      out.extra = "")
```

# Introduction

Nations have committed to protect a fixed portion of their EEZs in order to reduce and control anthropogenic impacts in the marine environment. Aichi target 11^[Aichi target 11 states that by 2020 10% of coastal and marine areas should be conserved through protected areas.] and target 14.5 of the United Nations Sustainable Development Goals^[Similarly, target 14.5 of the United Nations Sustainable Development Goals is to conserve at least 10% of coastal and marine areas.] aim to protect 10% of coastal and marine areas. Some more ambitious goals call for 30%, such as that from the World Parks Congress^[the International Union for the Conservation of Nature (IUCN) has suggested that at least 30% of each marine habitat should be protected in areas with no extractive activities.].

These goals ultimately aim to protect a global amount of biodiversity by spatially abating risks. However, costs and benefits are heterogeneous in space, and even conservation-minded countries might struggle to meet these targets if costs are prohibitive. But what if a nation could pay to conserve elsewhere, where the costs are lower? This setup is similar to that of pollution abatement in a multi-firm setting. A large body of theoretical and empirical literature has shown that an efficient way to achieve a level of pollution abatement is by leveraging differences in firm's marginal cost curves and incentivizing trade of emission permits.

Just as any two firms are capable of reducing their emissions by a given amount, two nations are capable of implementing MPAs with the same biodiversity value. However one nation (or firm) may be able to do so at a lower cost. A market approach may be the most efficient (*i.e.* cost-effective) way of balancing these differences in costs and benefits, and ultimately allow us to reach the desired targets at a reduced cost.

Under such a market, what would be the gains from trade? For the same amount of conservation as in the BAU scenario, how much are the costs reduced? How does spatially dividing the market (say, by ecosystem or ocean) change the outcome? This are indeed the questions that I seek to answer.

# Methods

We combine data on biodiversity benefit and costs to generate supply curves for each nation, as well as a global biodiversity supply curve. While in practice this approach can be used for any given biodiversity target, I produce an example using the 30% area-based target (*i.e.* We translate this area-based target into biodiversity units). We then find the trading price in the global supply curve and use the country-level supply curves to calculate in-situ and ex-situ conservation for every country. We can then calculate the differences in costs, and estimate the gains from trade.

The same approach can then be repeated for any level of spatial aggregation. As an example, I repeat the conservation excercise by subdividing the world into 12 Realms, and calculate realm-level supply curves to estimate the trading price for all countries that are part of that market.

The following sections go into more detail to describe my methods. The first section describes the data, and important caveats are mentioned at this stage. The second section describes how nation-level and aggregate supply curves were built. The third section dives into translating area-based targets into biodiversity benefit targets and the corresponding trading prices. Finally, we discuss how the analysis can be replicated by creating markets at different spatial scales.

## Data description

We must first identify the costs and benefits of conservation. Conserving biodiversity may provide benefits to society. For example, areas with higher species richness and biomass are more attractive to tourism \citep{williams_2000}. Species richness also leads to increased stability of ecosystems \citep{tilman_1995}, and may reduce exposure to pathogens \citep{lamb_2017}. The quantification is not straightforward, but we can assume that biodiversity indices are positively correlated with their benefits they provide (although saturation may occur past a given point).

I use spatially-explicit data on biodiversity benefit for each 50 X 50 km grid in the ocean. The score was derived to account for species richness and evolutionary distinctiveness, but also presence of topographic features (*e.g.* sea mounts). Figure \ref{fig:biodiversity-ranking} shows a global map of these values. The value of a given pixel (termed $\Delta v$) depends on previously protected pixels. As such, the value of a randomly chosen pixel is more or less meaningless. However, the configuration represented in Figure \ref{fig:biodiversity-ranking} was derived to maximize biodiversity. Therefore, protecting the best $n$ pixels and summing their values does represent the total amount of biodiversity protected. The same exercise has been done at the country-level (This is an important consideration for target calculations mentioned below. While I will use this global data for the purposes of motivating my approach, I do plan on using the appropriate data in my final work.)

![\label{fig:biodiversity-ranking} Global map of biodiversity ranking priorities. Higher values indicate higher priority to conserve.](results/img/benefit_map.png)

On the other hand, we need to quantify the costs associated to each pixel. An often-cited cost of implementing MPAs is that of losses in fisheries revenues \citep{smith_2010}. In this case, we define costs as losses in fisheries landings ^[I intend to use losses in fisheries revenues in the future. This will involve species-level changes in landings, as well as species-level price data. Essentially, the global losses in landings used here will be weighed by species price data.]. Since protection of some areas may lead to rebuilding fisheries, parts of the ocean might have negative costs. This means that there are gains to be made in conserving them. A map of global costs of conservation is shown in Figure \ref{fig:landing-losses}. As before, these data do not consider the transient dynamics, and represent the equilibrium state of protecting any given pixel.

![\label{fig:landing-losses} Global map showing the costs (losses in landings) from closing portions of the ocean. Negative values imply that there are gains to be made.](results/img/cost_map.png)

\FloatBarrier

## Building supply curves

Although there are important caveats, these data provide us with a way of calculating the costs and benefits of protecting any place under a nation's jurisdiction. While protecting the high seas may provide many benefits \citep{white_2014, sumaila_2015}, our market-based approach requires enforceable property rights, such as those offered by Exclusive Economic Zones. Moreover, biodiversity benefit is higher within Exclusive Economic Zones, where most of the species live \citep{mayorga_2020}. Therefore, we will ignore areas beyond national jurisdiction.

The next step is to identify which areas to protect. For two grid cells that provide equal biodiversity benefit, which one should be prioritized? This prioritization exercise need not be too complicated. We can assume that even if a country is seriously committed to conservation, costs must still be minimized. The most efficient thing to do is to protect the one that minimizes costs while maximizing biodiversity benefits. Therefore, we must calculate the benefit-cost ratio of each gridcell:

$$
BCR_i = \frac{B_i}{C_i}
$$

Where $B_i$ corresponds to the biodiversity benefit associated with protecting cell $i$, and $C_i$ corresponds to the costs of protecting cell $i$. We can do this calculation globally, and produce a map of BCR (Figure \ref{fig:bcr-map}). Due to the possibility of negative costs, the BCR may be negative. We must therefore differentiate the BCR of cells with negative and positive costs, and rank them in this nested way.

![\label{fig:bcr-map} Map of Benefit-Cost Ratio (BCR) within nation's Exclusive Economic Zones.](results/img/bcr_map.png)

For each country, we can rank the grid cells by their BCR and calculate the total biodiversity benefit and total costs of achieving that benefit. But more importantly, we can calculate the marginal costs (defined as the cost of protecting an extra unit of biodiversity: tonnes of fish lost / benefit unit), and produce a supply curve of conservation for each country. Their shape suggests that the first few units of conservation can be achieved at relatively low costs, but that it becomes increasingly costly to obtain more and more biodiversity benefits. Figure \ref{fig:eez-supply-curve} shows the biodiversity supply curves of each country, and the horizontally-summed global supply curve.

![\label{fig:eez-supply-curve}Supply curve for each country](results/img/eez_supply_curve.png)

## Finding targets and trading price

<!-- MAYBE:: A meta-analysis of simulation studies suggests that targets ranging from biodiversity protection to food provisioning can be indeed achieved by protecting ~30% of our coastal oceans \citep{oleary_2016,cabral_2019}. However, these area-based targets ultimately imply a desired level of biodiversity benefit. -->

The supply curves above will tell us the per-unit-costs of achieving a given amount of biodiversity benefit. But what is this "desired" amount of biodiversity benefit? All conservation targets are area-based, and do not explicitly call for an amount of conservation such as "protect 20 species", or "protect 3 habitats". However, we know the costs and benefits of each grid cell. This allows us to anticipate how rational nations may translate their area-based requirements into conservation interventions.

Figure \ref{fig:eez-supply-curve-approaches} shows five possible ways in which nations may reach an area-based target. Each panel shows the amount of biodiversity benefit produced by protecting a given percentage (x-axis) of a nation's EEZ. The only difference between panels is the strategy taken by nations, which leads to different curvatures. In the first panel, labeled as "efficient", nations conserve area in decreasing BCR values. The second panel maximizes conservation, and nations protect based on the biodiversity benefit rankings and completely ignore the costs. Similarly, the third panel seeks to maximize costs only, without accounting for how much conservation is achieved. The last two panels do the opposite, and try to minimize conservation or costs, without accounting for the other. The scenarios where costs are maximized or biodiversity benefits minimized are of course unlikely, however they provide bounds for where the true target lies. From now on, we will move forward with he efficient target of achieving 72 units of biodiversity benefit.

The most efficient way to achieve this level of conservation is by prioritizing places with a higher BCR. We can take the horizontally-summed global supply curve of biodiversity and find the corresponding costs for each of the benefit targets identified above (Figure \ref{fig:global-conservation-targets-and-trading-prices}). This values are also known as the trading price. A nation will continue to conserve in-situ up until the cost of an additional unit of conservation is equal to this value. Instead, it is more cost-effective to conserve elsewhere in the world where the costs are lower.

## Spatial considerations

When combining different data sources, we also include pixel-level information about the Hemisphere, Realm, Province, and Ecoregion in which they reside. This allows us to repeat the exercise of finding supply curves for any level of spatial division in order to simulate markets within them. This is better described in the results section, where I present detailed methods and results in parallel.

# Results

The main purpose of this project is to identify the gains from trade. But in order to get there, there are other minor findings that are worth mentioning here. This sections presents some preliminary results. The first section shows findings for a global market, where I calculate the gains from trade for a given target and it's corresponding trading price. I then turn to the realm-level markets, and present the same information for each realm. Whenever relevant, I mention opportunities for improvements, and I later discuss them in the discussion section.

## Global

By combining costs and benefits of conservation and anticipating the ways in which countries may conserve within their waters, we can translate the (percent) area-based targets into biodiversity benefit targets. We find that a 30% target yields a global biodiversity benefit of 3 to 106, depending on the approach taken (Figure \ref{fig:eez-supply-curve-approaches}; Table \ref{tab:trading-prices}).

![\label{fig:eez-supply-curve-approaches}Five sequential conservation approaches. Each line represents one nation. The y-axis shows how much conservation is achieved by protecting a given percentage (x-axis) of a nation's EEZ. The numbers show the totl biodiversity, summing across all nations.](results/img/eez_supply_curves_approaches.png)

\newpage

Our global supply curve allows us to take any biodiversity target and find its corresponding costs. In doing so, we can identify the trading price for any possible target. We find that the trading price for conservation lies between 0.08 and 483,528^[I must stress that these figures represent losses in fisheries landings, not dollars, and that more work needs to be done.]. Figure \ref{fig:global-conservation-targets-and-trading-prices} shows the corresponding trading prices for each of the targets outlined above. Table \ref{tab:trading-prices} shows the five targets and their trading prices. While these figures and table show only the values for the five approaches mentioned above, the same can be done for any given biodiversity target.

![\label{fig:global-conservation-targets-and-trading-prices} The global conservation supply curve, showing the costs for each of the biodiversity benefit targets.](results/img/global_conservation_targets_and_trading_prices.png)

\input{results/tab/trading-prices.tex}

\newpage

In translating the area-based target into a biodiversity benefit target we identified the global conservation benefits, but also the costs to each nation (Figure \ref{fig:equilibrium-supply-curves} left). We can use the nation-level supply curves and trading price to find the market's equilibrium for conservation (Figure \ref{fig:equilibrium-supply-curves} right). Under a market-based approach, in-situ conservation will decrease for some nations (those for which costs are higher than the trading price), while some may see increased in-situ conservation (those under the trading price). The additional conservation in some nations (red lines in Figure \ref{fig:equilibrium-supply-curves}) can only be achieved through a market, where nations whose in-situ conservation would exceed the trading price are willing to pay to conserve elsewhere.

![\label{fig:equilibrium-supply-curves} Supply curves for a case where nations efficiently conserve 30% in-situ (left) or with a market-based approach (right). The horizontal dashed line shows the trading price (131,241.92). Red lines in the right-side panel show the portion of additional conservation that is incentiviez by trade.](results/img/equilibrum_supply_curves.png)

By knowing the equilibrium under each approach we can compare the total costs and calculate the gains from trade. We find that a market-based approach can produce the same biodiversity benefit of 71.56 units for just 54% of the costs (Table \ref{tab:gains-from-trade}). Of course, gains from trade are heterogeneously distributed among nations. The map below (Figure \ref{fig:map-of-trade}) shows which countries would rather pay to conserve elsewhere, and which countries get paid to conserve in-place. Figure \ref{ref:two-states-map} shows the outcome of each approach.

\input{results/tab/gains_from_trade.tex}

![\label{fig:map-of-trade}Map of trade. Blue indicates nations that reach the trading price before meeting their target, and therefore chose to pay to conserve elsewhere. Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/map_of_trade.png)

![\label{ref:two-states-map} Map of two possible conservation outcomes.](results/img/two_states_map.png)

\newpage

## Realms

The results presented so far assume that a unit of biodiversity is worth the same anywhere around the world. However, we might want to ensure that no single type of habitat or region is left out. To overcome this, markets can be established at different spatial scales. Here, we use different scales of zoning in the marine environment (*i.e.* Biogeographic zoning). \citet{spalding_2007} divided the oceans using a hierarchical approach with Realms (n = 12) containing Provinces (n = 60), which in turn contain Ecoregions (n = 219).

The same approach as above can be repeated for any level of spatial aggregation that allows for more than one country. For example, this can be done for each of the 12 realms (Figure \ref{fig:realm-map}). Each Realm contains more than one nation, which would allow for trade to occur (Figure \ref{fig:eezs-per-realm}). For example, the Tropical Atlantic contains more than 60 nations, while Temperate Australasia contains just three. Any given country may also be part of more than one realm (Figure \ref{fig:realms-per-eezs}). For example, Mexico is present across four realms (Tropical Eastern Pacific, Temperate Northern Pacific, Temperate Northern Atlantic, and Tropical Atlantic).

As done before for the global analysis, we can generate the biodiversity supply curves of each country-realm combination, and calculate the realm-level supply curve for biodiversity benefit. Then, for any desired level of biodiversity benefit, we can estimate the realm-specific trading price, and derive the market equilibrium. From there, we can estimate the gains from trade, and identify who gains from this approach.

We first must find the target amount of biodiversity. We do this by finding how much biodiversity would be protected if every country were to protect 30% of each realm present within their Exclusive Economic Zone ^[This is more closely aligned with what the IUCN 30% target is: the International Union for the Conservation of Nature (IUCN) has suggested that at least 30% of each marine habitat should be protected in areas with no extractive activities.]. We then sum the realm-level biodiversity to obtain the aggregate biodiversity (Table \ref{tab:rlm-trading-prices}). Using the realm-level supply curves (Figure \ref{fig:eez-rlm-supply-curve} bottom) we can identify the trading prices. When the market is segmented by realms, a market approach produces the same amount of conservation for just 65.2% of the costs in the BAU scenario. The realm-level gains from trade for such a market are shown in Table \ref{tab:rlm-gains-from-trade}, and Figure \ref{fig:rlm-map-of-trade} shows the realm-level transactions. Note how for the Temperate Northern Pacific Mexico gets paid to conserve, while in the Tropical Atlantic it pays to conserve elsewhere.

So far, I have performed preliminary analyses for a global market and outlined how it would be done for 12 realms. I believe there is room (and need) to try a few more approaches. The first approach would involve "zooming out" to create four markets, one for each hemisphere. The second approach would then increase the scale by repeating the exercise for each ocean basin. Then, I would further increase the scale by taking the market at the province-level (Figure \ref{fig:eezs-per-province}). Doing it at the ecoregion-level (the next biogeographical scale) would yield less benefits from trade, since many Ecoregions contain only one nation. I expect gains from trade to decrease as spatial resolution (or segmentation of the markets) increases. In the end I will have six levels of spatial aggregation: global, hemisphere, ocean, realm, province, and EEZ (BAU).

![\label{fig:realm-map}Map of the 12 realms, as defined by \citet{spalding_2007}.](results/img/realm_map.png)

![\label{fig:eezs-per-realm} Number of nations contained within each of the realms described by \citet{spalding_2007}. The vertical dashed line lies at 2,  the minimum number of nations required for trade to occur.](results/img/eezs_per_realm.png)

![\label{fig:realms-per-eezs} Number of realms in each Exclusive Economic Zone](results/img/realms_per_eez.png)

![\label{fig:eez-rlm-supply-curve} Biodiversity supply curves for all nations within each realm (top panels), and realm-level biodiversity supply curves (bottom). For the small panels, each line represents a country. In the large bottom panel, each line represents the horizontally-summed supply curve for each realm (color coded).](results/img/eez_rlm_supply_curve.png)

\input{results/tab/rlm_trading_prices.tex}

\input{results/tab/rlm_gains_from_trade.tex}

![\label{fig:rlm-map-of-trade}Map of trade for each realm. Blue indicates nations that reach the trading price before meeting their target, and therefore chose to pay to conerve elsewhere. Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/rlm_map_of_trade.png)

\newpage

# Other figures and tables

![\label{fig:eezs-per-province} Number of Exclusive Economic Zones in each province](results/img/eezs_per_province.png)

![](results/img/eezs_per_ecoregion.png)

\clearpage

\bibliography{references}

### 2020-08-20 scripts/03_descriptive_content/02_plot_trading_units.R

@@ -152,7 +152,7 @@ eezs_per_ecoregion_plot <-
 # Export plots
 lazy_ggsave(plot = eezs_per_realm_plot,
             filename = "eezs_per_realm",
-            width = 15, height = 11)
+            width = 15, height = 8)
 
 # Export plots
 lazy_ggsave(plot = eezs_per_province_plot,

### 2020-08-20 scripts/04_analysis/01_get_targets.R

@@ -36,12 +36,52 @@ eez_h_sum_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_h_
   select(iso3, everything())
 
 # PROCESSING #############################################################################################
-# The procesing part sorts the dataset (ascending and descending) by the relevant variable (cost or benefit)
-# It then calculates the total benefit (using the "get_country_patwhays" function),
-# as well as the percentage contribution
+# The processing part sorts the dataset (ascending and descending) by the relevant variable (cost or benefit)
+# It then calculates the total benefit (using the "get_country_pathways" function),
+# as well as the percentage contribution. The process is done globally and for each country.
+
+## Global
+# Most efficient
+agg_cb <- eez_cb %>% 
+  arrange(desc(bcr)) %>% 
+  get_country_pathways() %>% 
+  mutate(type = "efficient")
 
 # Maximize conservation
-max_con <- eez_cb %>% 
+max_con_agg <- eez_cb %>% 
+  arrange(desc(benefit)) %>% 
+  get_country_pathways() %>% 
+  mutate(type = "maximize conservation")
+
+# Minimize conservation
+min_con_agg <- eez_cb %>% 
+  arrange(benefit)  %>% 
+  get_country_pathways() %>% 
+  mutate(type = "minimize conservation")
+
+# Maximize costs
+max_cos_agg <- eez_cb %>% 
+  arrange(desc(cost)) %>% 
+  get_country_pathways() %>% 
+  mutate(type = "maximize costs")
+
+# Minimize costs
+min_cos_agg <- eez_cb %>% 
+  arrange(cost) %>% 
+  get_country_pathways() %>% 
+  mutate(type = "minimize costs")
+
+# We now combine all curves together
+all_curves_agg <- rbind(
+  agg_cb,
+  max_con_agg,
+  min_con_agg,
+  max_cos_agg,
+  min_cos_agg)
+
+## National
+# Maximize conservation
+max_con_eez <- eez_cb %>% 
   group_by(iso3) %>% 
   arrange(desc(benefit)) %>% 
   nest() %>% 
@@ -51,7 +91,7 @@ max_con <- eez_cb %>%
   unnest(data)
 
 # Minimize conservation
-min_con <- eez_cb %>% 
+min_con_eez <- eez_cb %>% 
   group_by(iso3) %>% 
[…]

### 2020-09-16 scripts/04_analysis/03_get_eez_level_conservation.R
Renamed scripts, added scripts for 30% in each segment, added generalized script for all sgments and all scenarios

@@ -151,6 +151,18 @@ lazy_ggsave(plot = map_of_trade,
             width = 10,
             height = 5)
 
+percent_of_bau_costs <- gains_from_trade %>% 
+  filter(variable == "tc") %>% 
+  pull(ratio)
+
+gains_from_trade %>% 
+  select(variable, difference) %>% 
+  spread(variable, difference) %>% 
+  mutate(percent_of_bau = percent_of_bau_costs,
+         market = "global",
+         segments = 1L) %>% 
+  saveRDS(file = file.path(project_path, "output_data", "gains_from_trade_glb.rds"))
+
 gains_from_trade %>% 
   mutate(variable = c("Area", "Biodiversity benefits", "Total costs")) %>% 
   knitr::kable(format = "latex",

### 2020-09-16 scripts/04_analysis/04_hemisphere_level_market.R

@@ -60,7 +60,7 @@ mkt <- hem_eez_cb %>%
   left_join(hem_trading_prices, by = c("hemisphere")) %>%
   filter(mc <= trading_price) %>%              # Keep all patches in each country with a cost < trading price
   mutate(approach = "mkt") %>% 
-  select(-c(trading_price,))
+  select(-c(trading_price))
 
 ## Calculate country-level summaries
 # For BAU
@@ -110,7 +110,7 @@ benefit_supply_curves <- rbind(bau, mkt %>% select(-target)) %>%
   geom_hline(data = hem_trading_prices, aes(yintercept = trading_price), linetype = "dashed") +
   facet_grid(hemisphere ~ approach, scales = "free_y") +
   scale_color_brewer(palette = "Set1", direction = -1) +
-  # lims(y = c(-1000, 1000 * 5), x = c(0, 200)) +
+  lims(y = c(-1000, 100000 * 5), x = c(0, 5)) +
   ggtheme_plot() +
   labs(x = "Biodiversity",
        y = "Costs",
@@ -128,42 +128,60 @@ map_of_trade <- coast %>%
   ggplot() +
   geom_sf(data = coast) +
   geom_sf(aes(fill = gets_paid), color = "black", size = 0.1) +
-  facet_wrap(~hemisphere, ncol = 3) +
+  facet_wrap(~hemisphere, ncol = 2) +
   scale_fill_brewer(palette = "Set1", direction = -1) +
   ggtheme_map() +
   guides(fill = FALSE)
 
 # Plot the two states of the world
-# two_states_map <- 
-#   rbind(bau, mkt) %>% 
-#   ggplot() +
-#   geom_sf(data = coast) +
-#   geom_raster(aes(x = lon, y = lat, fill = benefit)) +
-#   facet_wrap(~approach, ncol = 1) +
-#   ggtheme_map() +
-#   scale_fill_viridis_c() +
-#   guides(fill = guide_colorbar(title = "Biodiversity",
-#                                frame.colour = "black",
-#                                ticks.colour = "black")) +
-#   labs(caption = "Both conservation strategies yield the same benefits,\nbut a market approach results in 1t4% of the costs")
+two_states_map <-
+  rbind(bau, mkt %>% select(-target)) %>%
+  ggplot() +
+  geom_sf(data = coast) +
+  geom_raster(aes(x = lon, y = lat, fill = benefit)) +
+  facet_wrap(~approach, ncol = 1) +
[…]

### 2020-09-16 scripts/04_analysis/05_realm_level_market.R

@@ -108,7 +108,7 @@ benefit_supply_curves <- rbind(bau, mkt %>% select(-target)) %>%
   geom_hline(data = rlm_trading_prices, aes(yintercept = trading_price), linetype = "dashed") +
   facet_grid(realm ~ approach, scales = "free_y") +
   scale_color_brewer(palette = "Set1", direction = -1) +
-  # lims(y = c(-1000, 1000 * 5), x = c(0, 200)) +
+  lims(y = c(-1000, 100000 * 5), x = c(0, 4)) +
   ggtheme_plot() +
   labs(x = "Biodiversity",
        y = "Costs",
@@ -132,36 +132,53 @@ map_of_trade <- coast %>%
   guides(fill = FALSE)
 
 # Plot the two states of the world
-# two_states_map <- 
-#   rbind(bau, mkt) %>% 
-#   ggplot() +
-#   geom_sf(data = coast) +
-#   geom_raster(aes(x = lon, y = lat, fill = benefit)) +
-#   facet_wrap(~approach, ncol = 1) +
-#   ggtheme_map() +
-#   scale_fill_viridis_c() +
-#   guides(fill = guide_colorbar(title = "Biodiversity",
-#                                frame.colour = "black",
-#                                ticks.colour = "black")) +
-#   labs(caption = "Both conservation strategies yield the same benefits,\nbut a market approach results in 1t4% of the costs")
+two_states_map <-
+  rbind(bau, mkt %>% select(-target)) %>%
+  ggplot() +
+  geom_sf(data = coast) +
+  geom_raster(aes(x = lon, y = lat, fill = benefit)) +
+  facet_wrap(~approach, ncol = 1) +
+  ggtheme_map() +
+  scale_fill_viridis_c() +
+  guides(fill = guide_colorbar(title = "Biodiversity",
+                               frame.colour = "black",
+                               ticks.colour = "black")) +
+  labs(caption = "Both conservation strategies yield the same benefits,\nbut a market approach costs 34.8% less")
 
 
 ## EXPORT FIGURES #########################################################################
 
-# lazy_ggsave(plot = benefit_supply_curves,
-#             filename = "equilibrum_supply_curves",
-#             width = 12,
-#             height = 6)
+lazy_ggsave(plot = benefit_supply_curves,
+            filename = "equilibrum_supply_curves_rlm",
+            width = 12,
+            height = 6)
 
-# lazy_ggsave(plot = two_states_map,
[…]

### 2020-09-16 scripts/04_analysis/06_province_level_market.R

@@ -100,71 +100,48 @@ gains_from_trade <- full_join(realized_mkt_cb, realized_bau_cb, by = c("iso3", "
          ratio = mkt / bau)
 
 ## FIGURES #########################################################################
-## Plot the supply curves where they stop
-benefit_supply_curves <- rbind(bau, mkt %>% select(-target)) %>%
-  left_join(stops, by = c("iso3", "province", "approach"), fill = list(mc_stop = 0)) %>% 
-  mutate(mkt_gain = mc >= mc_stop,
-         approach = ifelse(approach == "bau", "BAU", "Market")) %>% 
-  replace_na(replace = list(mkt_gain = F)) %>% 
-  ggplot(aes(x = tb, y = mc, group = iso3, color = mkt_gain)) +
-  geom_line(size = 0.2) +
-  geom_hline(data = pro_trading_prices, aes(yintercept = trading_price), linetype = "dashed") +
-  facet_grid(province ~ approach, scales = "free_y") +
-  scale_color_brewer(palette = "Set1", direction = -1) +
-  # lims(y = c(-1000, 1000 * 5), x = c(0, 200)) +
-  ggtheme_plot() +
-  labs(x = "Biodiversity",
-       y = "Costs",
-       caption = "NOTE: Axis have been cropped for visualization purposes") +
-  guides(color = FALSE)
-
 got_paid <- full_join(realized_mkt_cb, realized_bau_cb, by = c("province", "iso3")) %>% 
   select(-contains("app")) %>% 
   mutate(gets_paid = bau_tc <= mkt_tc)
 
-map_of_trade <- coast %>% 
-  left_join(got_paid, by = c("iso_a3" = "iso3")) %>% 
-  drop_na(province) %>%
-  replace_na(replace = list(gets_paid = FALSE)) %>% 
+# Plot the two states of the world
+two_states_map <-
+  rbind(bau, mkt %>% select(-target)) %>%
   ggplot() +
   geom_sf(data = coast) +
-  geom_sf(aes(fill = gets_paid), color = "black", size = 0.1) +
-  facet_wrap(~province, ncol = 3) +
-  scale_fill_brewer(palette = "Set1", direction = -1) +
+  geom_raster(aes(x = lon, y = lat, fill = benefit)) +
+  facet_wrap(~approach, ncol = 1) +
   ggtheme_map() +
-  guides(fill = FALSE)
-
-# Plot the two states of the world
[…]

### 2020-09-16 scripts/04_analysis/07_costs_avoided_for_each_mkt_segment.R

@@ -1,0 +1,29 @@
+
+
+
+library(purrr)
+library(tidyverse)
+
+
+files <- list.files(path = file.path(project_path, "output_data"),
+                    pattern = "gains_from_trade*")
+
+data <- file.path(file.path(project_path, "output_data", files)) %>% 
+  map_dfr(readRDS) %>% 
+  arrange(segments) %>% 
+  mutate(market = paste0(str_to_sentence(market), " (", segments, ")")) %>% 
+  mutate(market = fct_reorder(market, segments))
+
+
+segment_gains <- 
+  ggplot(data = data, 
+         mapping = aes(x = market, y = 1 - percent_of_bau)) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  labs(x = "Market level (# of segments)",
+       y = "% Costs avodided by market approach") +
+  ggtheme_plot()
+
+lazy_ggsave(plot = segment_gains,
+            filename = "segment_gains",
+            width = 10, height = 7.5)

### 2020-09-16 scripts/04_analysis/08_all_segments_all_scenarios.R

@@ -1,0 +1,239 @@
+#######################################################
+#
+#######################################################
+
+
+
+# SET UP ################################################################################################
+# Load packages
+library(startR)
+library(cowplot)
+library(tidyverse)
+
+# Load data
+eez_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_costs_and_benefits.rds")) %>% 
+  mutate(type = "efficient") %>% 
+  select(iso3, everything())
+eez_h_sum_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_h_sum_costs_and_benefits.rds")) %>% 
+  mutate(type = "efficient") %>% 
+  select(iso3, everything())
+
+hem_eez_cb <- readRDS(
+  file = file.path( project_path, "processed_data", "hem_eez_costs_and_benefits.rds")
+) 
+hem_h_sum <- readRDS(
+  file = file.path( project_path, "processed_data", "hem_h_sum_costs_and_benefits.rds")
+) 
+
+rlm_eez_cb <- readRDS(
+  file = file.path( project_path, "processed_data", "rlm_eez_costs_and_benefits.rds")
+) 
+rlm_h_sum <- readRDS(
+  file = file.path( project_path, "processed_data", "rlm_h_sum_costs_and_benefits.rds")
+) 
+
+pro_eez_cb <- readRDS(
+  file = file.path( project_path, "processed_data", "pro_eez_costs_and_benefits.rds")
+) 
+### Horizontally summed for each province
+pro_h_sum <- readRDS(
+  file = file.path( project_path, "processed_data", "pro_h_sum_costs_and_benefits.rds")
+) 
+
+
+get_market_gains <- function(eez_cb, r, trading_price) {
+  bau <- eez_cb %>% 
+    filter(pct <= r) %>%                       # Keep the most efficient 30% of each country - hemisphere
+    mutate(approach = "bau") %>% 
+    group_by(approach, iso3) %>% 
+    summarize(bau_tb = sum(benefit, na.rm = T),
+              bau_tc = sum(cost, na.rm = T),
+              mc_stop = max(mc, na.rm = T),
+              bau_area = n(),
+              .groups = "drop_last") %>% 
+    ungroup()
+  
+  mkt <- eez_cb %>% 
[…]

### 2020-12-09 scripts/00_setup/01_setup.R
Updated setup script and EEZ cleaning script to simplify using R, not system

@@ -6,7 +6,7 @@ sys_path <- ifelse(Sys.info()["sysname"]=="Windows", "~/G:/","~/Google Drive Fil
 # Nat geo ocean conservation priorities path
 ng_data_path <- file.path(sys_path,"Shared drives/emlab/projects/current-projects/ocean-conservation-priorities/data")
 # Path to our emLab's data folder
-data_path <- file.path(sys_path,"Shared drives/emlab/data/")
+data_path <- file.path(sys_path,"Shared drives/emlab/data")
 # Path to this projects directory
 project_path <- "~/Google Drive File Stream/Shared drives/emlab/projects/current-projects/transferable-conservation"
 

### 2020-12-09 scripts/01_cleaning/01_clean_EEZs.R

@@ -47,9 +47,9 @@ eez <- st_read(dsn = file.path(data_path,
   ungroup() %>%
   select(-a) %>% 
   st_make_valid() %>%
-  ms_simplify(keep_shapes = T, sys = T) %>% 
+  ms_simplify(keep_shapes = T) %>%
   st_make_valid() %>% 
-  st_transform(crs = proj_moll) %>%                 # Reproject to moll
+  st_transform(crs = proj_moll) %>%                   # Reproject to moll
   st_make_valid() %>% 
   mutate(iso3n = countrycode(iso3, "iso3c", "iso3n")) %>% 
   select(iso3, iso3n)

### 2020-12-09 scripts/02_processing/01_generate_pixel_benefits.R
Adding script to calculate species-level benefits

@@ -1,0 +1,56 @@
+library(raster)
+library(sf)
+library(tidyverse)
+
+source(here::here("common.R"))
+source(here::here("functions", "map_priorities.R"))
+
+# Load data 
+
+spp_files <- tibble(filepath = list.files(c(file.path(ng_data_path, "02_processed", "species_distributions", "birdlife"),
+                                            file.path(ng_data_path, "02_processed", "species_distributions", "aquamaps")),
+                                          full.names = T),
+                    valid_sci_name = str_replace_all(str_remove(basename(filepath), "\\.tif"), "_", " ")) %>% 
+  arrange(valid_sci_name)
+
+features_df <- stack(spp_files$filepath) %>%
+  raster::as.data.frame(xy = T) %>%
+  rownames_to_column(var = "cell_id") %>% 
+  # inner_join(ocean_matrix) %>%
+  select(x, y, cell_id, everything()) %>%
+  as_tibble()
+
+n_features <- nrow(spp_files) 
+
+
+## Normalize and trim
+
+features_matrix <- features_df %>% 
+  select(-x,-y,-cell_id) %>% 
+  as.matrix()
+
+metadata <- features_df %>% 
+  select(x, y, cell_id)
+
+Norm_features_matrix <- sweep(features_matrix, 2, colSums(features_matrix, na.rm = T), FUN = "/")
+
+rownames(Norm_features_matrix) <- features_df$cell_id
+
+# Norm_features_matrix <- Norm_features_matrix[rowSums(is.na(Norm_features_matrix)) != ncol(Norm_features_matrix), , drop = F]
+
+Norm_features_matrix[is.na(Norm_features_matrix)] <- 0
+
+saveRDS(Norm_features_matrix,
+        file = file.path(project_path, "processed_data", "norm_features_matrix.rds"))
+
+suitability_layer <- tibble(suitability = matrixStats::rowSums2(Norm_features_matrix),
+                            cell_id = rownames(Norm_features_matrix)) %>% 
+  left_join(metadata, by = "cell_id") %>% 
+  select(x, y, suitability) %>% 
+  mutate(suitability = suitability / max(suitability, na.rm = T)) %>%
+  rasterFromXYZ()
+
+plot(suitability_layer)
+
+writeRaster(x = suitability_layer, filename = file.path(project_path, "processed_data", "suitability.tif"))
+

### 2020-12-09 scripts/02_processing/02_rasterize_costs.R
Deleted old script using Ren's costs

@@ -1,35 +1,0 @@
-#  rasterize_rens_crap
-
-## SETUP #############################################################################
-# Load packages
-library(startR)
-library(raster)
-library(tidyverse)
-
-# Load data
-# Benefits raster as a reference raster
-benefits_raster <- raster(
-  file.path(
-    ng_data_path,
-    "03_output/05_spp_wts_smts_provs_MPAs/ranking_raster.tif"
-  )
-)
-
-## PROCESSING #######################################################################
-# Costs raster
-costs_raster <-
-  readRDS(file = file.path(project_path, "raw_data", "Fig1_PixelLeveDH_raw.rds")) %>% 
-  rasterFromXYZ(crs = proj_moll) %>%                                                   # Rasterize
-  projectRaster(benefits_raster)                                                       # Reproject to fit resolution
-
-# Export raster #####################################################################
-writeRaster(x = costs_raster,
-            filename = file.path(
-              project_path,
-              "processed_data",
-              "costs_raster.tif"),
-            overwrite = T
-)
-
-
-# END OF SCRIPT

### 2020-12-09 scripts/02_processing/04_get_costs_and_benefits.R
renamed script to follow order

@@ -33,8 +33,12 @@ library(tidyverse)
 benefits_raster <-
   raster(
     file.path(
-      ng_data_path,
-      "03_output/05_spp_wts_smts_provs_MPAs/delta_v_raster.tif"
+      project_path,
+      # "03_output/05_spp_wts_smts_provs_MPAs/delta_v_raster.tif"
+      # "02_processed/species_richness/spp_richness.tif"
+      # "03_output/01_spp/ranking_raster.tif"
+      "processed_data",
+      "suitability.tif"
     )
   )
 
@@ -69,8 +73,7 @@ eez_meow <-
 ## PROCESSING ########################################################################
 # Extract codes for each pixel
 cb <-
-  stack(iso3n,
-        # Start by creating a raster stack of all features
+  stack(iso3n,                   # Start by creating a raster stack of all features
         rlm_code,
         pro_code,
         eco_code,
@@ -84,7 +87,7 @@ cb <-
     rlm_code = rlm_raster,
     pro_code = pro_raster,
     eco_code = eco_raster,
-    benefit = delta_v_raster,
+    benefit = suitability,
     cost = costs_raster
   ) %>%
   drop_na(iso3n, cost, benefit) %>%              # Drop areas beyond national jurisdiction

### 2020-12-09 scripts/04_analysis/07_costs_avoided_for_each_mkt_segment.R
Added missing package

@@ -1,6 +1,6 @@
 
 
-
+library(startR)
 library(purrr)
 library(tidyverse)
 

### 2020-12-11 scripts/00_setup/01_setup.R
Hide annoying dplyr messages

@@ -10,6 +10,12 @@ data_path <- file.path(sys_path,"Shared drives/emlab/data")
 # Path to this projects directory
 project_path <- "~/Google Drive File Stream/Shared drives/emlab/projects/current-projects/transferable-conservation"
 
+# Source project functions
+source(here::here("scripts", "00_setup","02_functions.R"))
+
+# Turn off dplyr's anoying messages
+options(dplyr.summarise.inform = FALSE)
+
 
 ###########################
 ## Useful general values ##
@@ -25,6 +31,9 @@ epsg_longlat <- 4326
 # A color palete
 zis_con <- wesanderson::wes_palette("Zissou1", 100, type = "continuous")
 
+##########################
+## Plot-related things ##
+##########################
 # Default geometry colors, fills, and shapes
 library(ggplot2)
 update_geom_defaults(geom = "col", list(color = "black",
@@ -43,5 +52,3 @@ update_geom_defaults(geom = "sf", list(color = "transparent",
                                        size = 0.3))
 
 
-# Source project functions
-source(here::here("scripts", "00_setup","02_functions.R"))

### 2020-12-11 scripts/02_processing/02_generate_pixel_costs.R
Added first pass to generate pixel costs

@@ -1,0 +1,103 @@
+
+
+# Load packages
+library(raster)
+library(data.table)
+library(tidyverse)
+
+# Create common pointer to RegWatson data
+rw_path <- file.path(data_path, "reg-watson-global-marine-capture", "global_fisheries_landing_v4")
+
+# Read in catch data
+## List the files
+ind <- list.files(path = file.path(rw_path, "industrial"),
+                          pattern = "*.csv",
+                          full.names = T) %>% 
+  tail(2)
+
+Nind <- list.files(path = file.path(rw_path, "nonindustrial"),
+                    pattern = "*.csv",
+                    full.names = T) %>% 
+  tail(2)
+
+
+catch_files <- c(ind, Nind)
+
+# Read all
+dt <- map_dfr(catch_files, fread, sep = ",")
+setkey(dt , Cell, ID)
+
+# Read in the codes
+cell_codes <- readxl::read_excel(file.path(rw_path, "Codes.xlsx"), sheet = 1L) %>% 
+  as.data.table(key = "Cell")
+
+taxa_codes <- readxl::read_excel(file.path(rw_path, "Codes.xlsx"), sheet = 3L) %>% 
+  select(TaxonKey, TaxonName) %>% 
+  mutate(price = 1:nrow(.))
+
+# Read indices
+index <- list.files(rw_path, "*.csv", full.names = T) %>% 
+  map_dfr(fread, key = "ID") %>% 
+  .[, ":=" (Year = IYear, TaxonKey = Taxonkey)] %>%
+  .[Year >= 2010, .(ID, Year, TaxonKey)]
+  
+
+merged <- dt %>% 
+  merge(index, all.x = TRUE, by = "ID") %>% 
+  merge(taxa_codes, all.x = TRUE, by = "TaxonKey") %>% 
+  merge(cell_codes, all.x = TRUE, by = "Cell")
+
+setkey(merged, Year, Cell)
+
+summary <- merged %>% 
+  .[!is.na(price)] %>% 
+  .[, .(Reported = sum(Reported, na.rm = T),
+        Revenue = sum(Reported * price, na.rm = T)),
+    by = .(Year, Cell, LatCentre, LonCentre)] %>%
+  .[,.(Reported = mean(Reported, na.rm = T),
+       Revenue = mean(Revenue, na.rm = T)),
+    by = .(Cell, LatCentre, LonCentre)]
+
+benefits_raster <-
+  raster(
+    file.path(
+      project_path,
[…]

### 2020-12-11 scripts/02_processing/04_get_costs_and_benefits.R
Cleanup raster reading, and make flexible to incorporate multiple costs

@@ -34,23 +34,24 @@ benefits_raster <-
   raster(
     file.path(
       project_path,
-      # "03_output/05_spp_wts_smts_provs_MPAs/delta_v_raster.tif"
-      # "02_processed/species_richness/spp_richness.tif"
-      # "03_output/01_spp/ranking_raster.tif"
       "processed_data",
       "suitability.tif"
     )
   )
 
 # Costs raster
-costs_raster <-
+catch_raster <-
   raster(
     file.path(
       project_path,
       "processed_data",
-      "costs_raster.tif"
+      "catch_raster.tif"
     )
   )
+
+# effort_raster
+# revenue_raster
+
 
 # Load spatial metadata rasters
 iso3n <-
@@ -78,7 +79,7 @@ cb <-
         pro_code,
         eco_code,
         benefits_raster,
-        costs_raster) %>%
+        catch_raster) %>%
   as.data.frame(xy = T) %>%       # Convert to data.frame, but keep coordinates
   rename(                         # Select and rename columns
     lon = x,
@@ -88,9 +89,9 @@ cb <-
     pro_code = pro_raster,
     eco_code = eco_raster,
     benefit = suitability,
-    cost = costs_raster
+    cost1 = catch_raster
   ) %>%
-  drop_na(iso3n, cost, benefit) %>%              # Drop areas beyond national jurisdiction
+  drop_na(iso3n, cost1, benefit) %>%                             # Drop areas beyond national jurisdiction
   mutate(hemisphere = case_when(lon > 0 & lat > 0 ~ "NE",
                                 lon < 0 & lat > 0 ~ "NW",
                                 lon > 0 & lat <= 0 ~ "SE",
@@ -101,12 +102,12 @@ master_data <- eez_meow %>%
   st_drop_geometry() %>%
   select(iso3, ecoregion, province, realm, iso3n, contains("code")) %>%
   left_join(cb, by = c("iso3n", "rlm_code", "pro_code", "eco_code")) %>%            # Join to the data.frame from rasters
-  select(lon, lat, iso3, ecoregion, province, realm, hemisphere, benefit, cost) %>% # Select columns
+  select(lon, lat, iso3, ecoregion, province, realm, hemisphere, benefit, cost1) %>% # Select columns
   filter(benefit >= 1e-6) %>% 
-  mutate(bcr = benefit / cost,                                                       # Calculate marginal benefit
-         mc = cost / benefit,
-         neg = bcr >= 0) %>%                                                         # Create dummy variable for negative costs
[…]

### 2020-12-11 scripts/04_analysis/08_all_segments_all_scenarios.R
Modified plots for proposal

@@ -200,31 +200,33 @@ gains_from_trade_multiple_scenarios <- rbind(
   gains_from_trade_multiple_scenarios_hem,
   gains_from_trade_multiple_scenarios_rlm,
   gains_from_trade_multiple_scenarios_pro
-  )
+  ) %>% 
+  mutate(market = stringr::str_to_sentence(market),
+         market = fct_relevel(market, "Province", after = Inf))
 
 # Visualize 
-abs <- ggplot(gains_from_trade_multiple_scenarios, aes(x = targets, y = difference, color = market)) +
+abs <- ggplot(gains_from_trade_multiple_scenarios, aes(x = targets / max(targets), y = difference, color = market)) +
   geom_line(size = 1) +
   ggtheme_plot() +
-  labs(x = "Biodiversity", 
+  labs(x = "% Biodiversity protected", 
        y = "Costs avoided (BAU - MKT)",
        color = "Segment") +
-  # scale_x_continuous(labels = scales::percent) +
+  scale_x_continuous(labels = scales::percent) +
   scale_color_brewer(palette = "Set1") +
   theme(legend.justification = c(0, 1),
         legend.position = c(0, 1))
 
-rel <- ggplot(gains_from_trade_multiple_scenarios, aes(x = targets, y = 1 - ratio, color = market)) +
+rel <- ggplot(gains_from_trade_multiple_scenarios, aes(x = targets / max(targets), y = 1 - ratio, color = market)) +
   geom_line(size = 1) +
   ggtheme_plot() +
-  labs(x = "Biodiversity", 
+  labs(x = "% Biodiversity protected", 
        y = "Costs avoided (difference / BAU)") +
-  # scale_x_continuous(labels = scales::percent) +
+  scale_x_continuous(labels = scales::percent) +
   scale_y_continuous(labels = scales::percent) +
   scale_color_brewer(palette = "Set1") +
   theme(legend.position  = "None")
 
-gain_from_trade_segmented_market_plot <- plot_grid(abs, rel, ncol = 2)
+gain_from_trade_segmented_market_plot <- plot_grid(abs, rel, ncol = 2, labels = "AUTO")
 
 lazy_ggsave(plot = gain_from_trade_segmented_market_plot,
             file = "gain_from_trade_segmented_market_plot",

### 2021-02-18 scripts/02_processing/02_combine_catch_and_prices.R
Updated exvessel cleaning to keep years

@@ -1,7 +1,9 @@
 
 # Load packages
-library(tidyverse)
 library(rfishbase)
+library(corrplot)
+library(tidyverse)
+
 
 # Set up taxonomy baseline
 ## Get taxonomy from SeaLifeBase
@@ -64,7 +66,7 @@ taxonomy_order_class <- taxonomy %>%
   slice(n = 1) %>% 
   ungroup()
 
-
+# Read-in price data and perform high-level data cleaning
 price <- read.csv(
   file.path(
     clean_seafod_path,
@@ -73,7 +75,7 @@ price <- read.csv(
   stringsAsFactors = F) %>% 
   as_tibble() %>% 
   janitor::clean_names() %>% 
-  filter(year == 2017) %>% 
+  filter(between(year, 2005, 2015)) %>% 
   filter_all(all_vars(!str_detect(., "[fF]reshwater|FRESHWATER"))) %>% 
   select(-x) %>% 
   drop_na(exvessel) %>% 
@@ -86,9 +88,13 @@ price <- read.csv(
          asfis_species = str_remove_all(asfis_species, "\\(.*\\)"),
          asfis_species = str_remove_all(asfis_species, "[:punct:]"),
          asfis_species = str_squish(asfis_species),
-         asfis_species = str_trim(asfis_species)) %>% 
-  rename(species = scientific_name) %>% 
-  mutate(species = my_validate(species)) %>% 
+         asfis_species = str_trim(asfis_species)) 
+
+# Take only the species data, and validate the scientific names and all taxonomy
+validated_taxonomy <- price %>% 
+  select(scientific_name) %>% 
+  distinct() %>% 
+  mutate(species = my_validate(scientific_name)) %>% 
   mutate(genus = str_extract(species, pattern = "^[:alpha:]+")) %>% 
   left_join(taxonomy_genus_family, by = "genus") %>% 
   mutate(family = ifelse(is.na(family) & genus %in% families, genus, family)) %>% 
@@ -99,48 +105,54 @@ price <- read.csv(
   mutate(genus = ifelse(genus == family, NA_character_, genus),
          genus = ifelse(genus == order, NA_character_, genus),
          genus = ifelse(genus == class, NA_character_, genus))
+  
+# Now we need to create a list of cases where "species" is not actually "species", but a higher taxon.
+# Leaving them in would be as double-counting.
 
-redundant_prices_species_genus <- price %>%
+# Find cases where species is actually a genus
[…]

### 2021-02-18 draft.Rmd
Updating draft

@@
 subtitle: "Draft"
+# https://stackoverflow.com/questions/52918716/authors-and-affiliations-in-the-yaml-of-rmarkdown
 author:
-  - "Juan Carlos Villaseñor-Derbez"
-  - "Darcy Bradley"
-  - "Christopher Costello"
-  - "Juan Mayorga"
-  - "Andrew Plantinga"
+  - Juan Carlos Villaseñor-Derbez:
+      email: juancarlos@ucsb.edu
+      institute: bren
+      correspondence: true
+  - name: Darcy Bradley
+    institute: bren
+  - name: Christopher Costello
+    institute: bren
+  - name: Juan Mayorga
+    institute: bren
+  - name: Andrew Plantinga
+    institute: bren
+institute:
+  - bren: Bren School of Environmental Science and Management, University of California Santa Barbara
 date: "Prepared on `r format(Sys.time(), '%B %d, %Y')`"
@@
     toc: no
+    pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
 header-includes:
@@
 ```
+
+\clearpage
+
+# Important sentences
+
+Importantly, the quality of a patch can be defined independently of other pixels.
+This is true for habitat suitability, in which the abiotic characteristics that determine the suitability of a patch are independent of the protected status of any patch.
 
@@
 
-\input{results/tab/rlm_trading_prices.tex}
+\input{results/tab/trading_prices_rlm.tex}
 
-\input{results/tab/rlm_gains_from_trade.tex}
+\input{results/tab/gains_from_trade_rlm.tex}
 

### 2021-02-19 scripts/02_processing/02_combine_catch_and_prices.R
Added year-based hierarchy to data merging

@@ -157,9 +157,9 @@ updated_price <- price %>%
 summarize_group <- function(x, group) {
   varname <- paste0(group, c("_median"))
   x %>% 
-    group_by_at(vars(one_of(group))) %>% 
+    group_by_at(vars(one_of(group, "year"))) %>% 
     summarize(median = median(exvessel, na.rm = T)) %>% 
-    magrittr::set_colnames(c(group, varname)) %>% 
+    magrittr::set_colnames(c(group, "year", varname)) %>% 
     drop_na()
 }
 
@@ -188,27 +188,28 @@ price_isscaap_group <- updated_price %>%
   summarize_group("isscaap_group")
 
 # We also know that the Watson dataset contains a "marine animals" category, whic in this case we'll
-# impute using the overal median value, for lack of a better value
+# impute using the overall median value, for lack of a better value
 marine_animals_median <- updated_price %>% 
-  select(species, exvessel) %>% 
+  select(species, year, exvessel) %>% 
   distinct() %>% 
-  pull(exvessel) %>% 
-  median(na.rm = T)
+  group_by(year) %>% 
+  summarize(marine_animals_median = median(exvessel, na.rm = T)) %>% 
+  ungroup() %>% 
+  mutate(species = "Marine animals")
 
 # Check correlation between these
 all_prices <- updated_price %>% 
-  left_join(price_species, by = "species") %>% 
-  left_join(price_genus, by = "genus") %>% 
-  left_join(price_family, by = "family") %>% 
-  left_join(price_order, by = "order") %>% 
-  left_join(price_class, by = "class") %>% 
-  left_join(price_isscaap_group, by = "isscaap_group") %>%
+  left_join(price_species, by = c("species", "year")) %>% 
+  left_join(price_genus, by = c("genus", "year")) %>% 
+  left_join(price_family, by = c("family", "year")) %>% 
+  left_join(price_order, by = c("order", "year")) %>% 
+  left_join(price_class, by = c("class", "year")) %>% 
+  left_join(price_isscaap_group, by = c("isscaap_group", "year")) %>%
   select(contains("median")) %>% 
   magrittr::set_colnames(value = str_replace_all(str_remove_all(colnames(.), "_median"), "_", " "))
 
 correlogram <- all_prices %>%
   magrittr::set_colnames(value = str_to_sentence(colnames(.))) %>%
-  # rename(Original = Exvessel) %>%
   cor(use = "pairwise.complete.obs") %>%
   ggcorrplot(type = "lower",
[…]

### 2021-02-19 scripts/02_processing/03_generate_pixel_costs.R
Updated pixel costs with annual average (2005 - 2015)

@@ -10,48 +10,47 @@ library(tidyverse)
 ind <- list.files(path = file.path(rw_path, "industrial"),
                           pattern = "*.csv",
                           full.names = T) %>% 
-  tail(2)
+  tail(3)
 
 Nind <- list.files(path = file.path(rw_path, "nonindustrial"),
                     pattern = "*.csv",
                     full.names = T) %>% 
-  tail(2)
+  tail(3)
 
 
 catch_files <- c(ind, Nind)
 
 # Read all
-dt <- map_dfr(catch_files, fread, sep = ",")
-setkey(dt , Cell, ID)
+dt <- map_dfr(catch_files, fread, sep = ",", key = c("Cell", "ID")) %>% 
+  .[, .(ID, Cell, Reported)]
 
 # Read in the codes
 cell_codes <- readxl::read_excel(file.path(rw_path, "Codes.xlsx"), sheet = 1L) %>% 
+  select(-OceanAreasqkm) %>% 
   as.data.table(key = "Cell")
 
 taxa_codes <- readRDS(file.path(project_path, "processed_data", "taxa_codes_and_prices.rds")) %>% 
-  data.table::data.table(key = "taxon_key")
+  select(year, taxon_key, price) %>% 
+  data.table::data.table(key = c("taxon_key", "year"))
 
 # Read indices
 index <- list.files(rw_path, "*.csv", full.names = T) %>% 
   map_dfr(fread, key = "ID") %>% 
-  .[, ":=" (Year = IYear, TaxonKey = Taxonkey)] %>%
-  .[Year >= 2010, .(ID, Year, TaxonKey)]
-  
+  .[, .(ID, year = IYear, taxon_key = Taxonkey)]
+
 
 merged <- dt %>% 
-  merge(index, all.x = TRUE, by = "ID") %>% 
-  merge(taxa_codes, all.x = TRUE, by.x = "TaxonKey", by.y = "taxon_key") %>% 
-  merge(cell_codes, all.x = TRUE, by = "Cell")
+  merge(index, all.x = TRUE, by = "ID") %>%
+  merge(taxa_codes, all.x = TRUE, by = c("taxon_key", "year"))
 
-setkey(merged, Year, Cell)
+setkey(merged, year, Cell)
 
 summary <- merged %>% 
-  .[, .(Reported = sum(Reported, na.rm = T),
-        Revenue = sum(Reported * price, na.rm = T)),
-    by = .(Year, Cell, LatCentre, LonCentre)] %>%
[…]

### 2021-03-10 scripts/99_others/01_draw_dummy_supply_curves.R
Added script that creates dummy supply curves and market explanation

@@ -1,0 +1,43 @@
+library(startR)
+library(cowplot)
+library(tidyverse)
+
+data <- expand_grid(
+  n = c("A", "B"),
+  q = seq(0, 10, by = 0.1)
+) %>% 
+  mutate(p = ifelse(n == "A", 1 * q, 2 * q)) %>% 
+  group_by(n) %>% 
+  ungroup()
+
+(p1 <- ggplot(data = data, aes(x = q, y = p, color = n)) +
+  geom_line(size = 1, linetype = "dashed") +
+  geom_line(data = filter(data, q <= 5), size = 1) +
+  scale_color_brewer(palette = "Set1") +
+  theme_half_open() +
+  labs(x = "Conservation (q)", y = "Marginal Costs (p)") +
+  geom_segment(x = 5, xend = 5, y = 0, yend = 25, color = "black", linetype = "dashed") +
+  geom_segment(x = 0, xend = 5, y = 5, yend = 5, linetype = "dashed", color = "red") +
+  geom_segment(x = 0, xend = 5, y = 10, yend = 10, linetype = "dashed", color = "steelblue") +
+  scale_x_continuous(expand = c(0, 0), breaks = c(5), labels = c("q"), limits = c(0, 7.5)) +
+  scale_y_continuous(expand = c(0, 0), breaks = c(5, 10), labels = c("p", expression(p + Delta)), limits = c(0, 15)) +
+  theme(legend.justification = c(0, 1),
+        legend.position = c(0.1, 1)) +
+  guides(color = guide_legend(title = "Nation")))
+
+(p2 <- ggplot(data = data, aes(x = q, y = p, color = n)) +
+  geom_line(size = 1, linetype = "dashed") +
+  geom_line(data = filter(data, p <= 6.7), size = 1) +
+  scale_color_brewer(palette = "Set1") +
+  theme_half_open() +
+  labs(x = "Conservation (q)", y = "Marginal Costs (p)") +
+  geom_segment(x = 3.35, xend = 3.35, y = 0, yend = 25, color = "steelblue", linetype = "dashed") +
+  geom_segment(x = 6.7, xend = 6.7, y = 0, yend = 25, color = "red", linetype = "dashed") +
+  geom_segment(x = 0, xend = 6.7, y = 6.7, yend = 6.7, linetype = "dashed", color = "black") +
[…]

### 2021-03-10 scripts/00_setup/01_setup.R
Deleted unused palette

@@ -33,9 +33,6 @@ proj_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "             
 epsg_moll <- "ESRI:54009"
 epsg_longlat <- 4326
 
-# A color palete
-zis_con <- wesanderson::wes_palette("Zissou1", 100, type = "continuous")
-
 ##########################
 ## Plot-related things ##
 ##########################

### 2021-03-10 scripts/04_analysis/03_get_eez_level_conservation.R
Fixed non-consrving nations and updated figure

@@ -33,9 +33,26 @@ trading_prices <- readRDS(
 
 # Load a coastline
 coast <- ne_countries(returnclass = "sf") %>% 
-  st_transform(crs = epsg_moll) 
+  st_transform(crs = epsg_moll) %>% 
+  mutate(in_mkt = iso_a3 %in% unique(eez_cb$iso3))
+
+# Load EEZ geopackage
+eez <- st_read(
+  file.path(project_path,
+            "processed_data",
+            "clean_world_eez_v11.gpkg")
+  ) %>% 
+  mutate(has_obligations = iso3 %in% unique(eez_cb$iso3)) %>% 
+  rmapshaper::ms_simplify(keep_shapes = T, sys = T) %>% 
+  st_make_valid() %>% 
+  filter(iso3 %in% unique(eez_cb$iso3))
 
 # PROCESSING ############################################################################################
+
+## Set up a data.frame of nation ISO3s that participate
+conserving_nations <- eez_cb %>% 
+  select(iso3) %>% 
+  distinct()
 
 ## Identify conserved patches
 # Get the most efficient trading price
@@ -45,7 +62,10 @@ trading_price <- trading_prices %>%
 
 # Filter to keep only the protected places
 bau <- eez_cb %>% 
-  filter(pct <= 0.3) %>%                       # Keep the most efficient 30$ of each country
+  group_by(iso3) %>% 
+  mutate(min_pct = min(pct, na.rm = T)) %>% 
+  ungroup() %>% 
+  filter(pct <= 0.3 | min_pct > 0.3) %>%      # Keep the most efficient 30% of each country OR the first patch
   mutate(approach = "bau")
   
 mkt <- eez_cb %>% 
@@ -59,7 +79,7 @@ realized_bau_cb <- bau %>%
   summarize(bau_tb = sum(benefit, na.rm = T),
             bau_tc = sum(cost, na.rm = T),
             mc_stop = max(mc, na.rm = T),
-            bau_area = n()) %>% 
+            bau_area = n() * 2500) %>% 
   ungroup()
 
 # For a market
@@ -67,17 +87,29 @@ realized_mkt_cb <- mkt %>%
   group_by(approach, iso3) %>% 
   summarize(mkt_tb = sum(benefit, na.rm = T),
             mkt_tc = sum(cost, na.rm = T),
-            mkt_area = n()) %>% 
+            mkt_area = n() * 2500) %>% 
   ungroup()
 
-# Find stopping prices
[…]

### 2021-03-10 scripts/99_others/01_draw_dummy_supply_curves.R
Updated dummy figure name

@@ -40,4 +40,4 @@ data <- expand_grid(
 
 
 cowplot::plot_grid(p1, p2, ncol = 2, labels = c(1, 2)) %>% 
-  lazy_ggsave(filename = "dummy_supply_curves.pdf", width = 6, height = 2.5)
+  lazy_ggsave(filename = "dummy_supply_curves", width = 6, height = 2.5)

### 2021-03-16 scripts/04_analysis/03_get_eez_level_conservation.R
Updated for presentation

@@ -65,7 +65,7 @@ bau <- eez_cb %>%
   group_by(iso3) %>% 
   mutate(min_pct = min(pct, na.rm = T)) %>% 
   ungroup() %>% 
-  filter(pct <= 0.3 | min_pct > 0.3) %>%      # Keep the most efficient 30% of each country OR the first patch
+  filter(pct <= 0.3 | pct <= min_pct) %>%      # Keep the most efficient 30% of each country OR the first patch
   mutate(approach = "bau")
   
 mkt <- eez_cb %>% 
@@ -119,26 +119,6 @@ gains_from_trade <- combined_outcomes %>%
   mutate(difference = bau - mkt,
          ratio = mkt / bau)
 
-## FIGURES #########################################################################
-## Plot the supply curves where they stop
-benefit_supply_curves <- rbind(bau, mkt) %>%
-  left_join(stops, by = c("iso3", "approach"),
-            fill = list(mc_stop = 0, mkt_tb = 0, mkt_tc = 0, mkt_area = 0)) %>% 
-  mutate(mkt_gain = mc >= mc_stop,
-         approach = ifelse(approach == "bau", "BAU", "Market")) %>% 
-  replace_na(replace = list(mkt_gain = F)) %>%
-  ggplot(aes(x = pct, y = mc, group = iso3, color = mkt_gain)) +
-  geom_line(size = 0.2) +
-  geom_hline(yintercept = trading_price, linetype = "dashed") +
-  facet_wrap(~approach, scales = "free_y") +
-  scale_color_brewer(palette = "Set1", direction = -1) +
-  # lims(y = c(0, trading_price * 2)) +
-  ggtheme_plot() +
-  labs(x = "Biodiversity",
-       y = "Marginal Costs",
-       caption = "NOTE: Axis have been cropped for visualization purposes") +
-  guides(color = FALSE)
-
 got_paid <- combined_outcomes %>% 
   mutate(gets_paid = mc_stop <= trading_price,
          mkt_gains = bau_tc - mkt_tc) %>% 
@@ -152,6 +132,45 @@ got_paid <- combined_outcomes %>%
 eez_with_results <- eez %>% 
   left_join(got_paid, by = "iso3")
 
+## FIGURES #########################################################################
+## Plot the supply curves where they stop
+benefit_supply_curves <- bau %>% 
+  select(-min_pct) %>% 
+  rbind(mkt) %>%
+  left_join(stops, by = c("iso3", "approach"),
[…]

### 2021-03-16 scripts/04_analysis/04_hemisphere_level_market.R

@@ -32,6 +32,17 @@ hem_h_sum <- readRDS(
 coast <- ne_countries(returnclass = "sf") %>% 
   st_transform(crs = epsg_moll) 
 
+# Load EEZ geopackage
+eez <- st_read(
+  file.path(project_path,
+            "processed_data",
+            "clean_world_eez_v11.gpkg")
+) %>% 
+  mutate(has_obligations = iso3 %in% unique(hem_eez_cb$iso3)) %>% 
+  rmapshaper::ms_simplify(keep_shapes = T, sys = T) %>% 
+  st_make_valid() %>% 
+  filter(iso3 %in% unique(hem_eez_cb$iso3))
+
 # PROCESSING ############################################################################################
 
 # Get targets
@@ -48,19 +59,26 @@ hem_trading_prices <- hem_h_sum %>%
   mutate(trading_price = map2_dbl(.x = target, .y = data, get_trading_price)) %>% 
   select(-data)
 
+## Set up a data.frame of nation ISO3s that participate
+conserving_nations <- hem_eez_cb %>% 
+  select(iso3, hemisphere) %>% 
+  distinct()
+
 ## Identify conserved patches
 # Get the most efficient trading price
 
 # Filter to keep only the protected places
 bau <- hem_eez_cb %>% 
-  filter(pct <= 0.3) %>%                       # Keep the most efficient 30% of each country - hemisphere
+  group_by(iso3, hemisphere) %>% 
+  mutate(min_pct = min(pct, na.rm = T)) %>% 
+  ungroup() %>% 
+  filter(pct <= 0.3 | pct <= min_pct) %>%                       # Keep the most efficient 30% of each country - hemisphere
   mutate(approach = "bau")
 
 mkt <- hem_eez_cb %>% 
   left_join(hem_trading_prices, by = c("hemisphere")) %>%
   filter(mc <= trading_price) %>%              # Keep all patches in each country with a cost < trading price
-  mutate(approach = "mkt") %>% 
-  select(-c(trading_price))
+  mutate(approach = "mkt")
 
 ## Calculate country-level summaries
 # For BAU
@@ -69,27 +87,40 @@ realized_bau_cb <- bau %>%
   summarize(bau_tb = sum(benefit, na.rm = T),
             bau_tc = sum(cost, na.rm = T),
[…]

### 2021-03-16 scripts/04_analysis/05_realm_level_market.R

@@ -30,6 +30,21 @@ rlm_h_sum <- readRDS(
 coast <- ne_countries(returnclass = "sf") %>% 
   st_transform(crs = epsg_moll) 
 
+# Load EEZ geopackage
+eez <- st_read(
+  file.path(project_path,
+            "processed_data",
+            "intersected_eez_and_meow.gpkg")
+) %>% 
+  mutate(has_obligations = iso3 %in% unique(rlm_eez_cb$iso3)) %>%
+  rmapshaper::ms_simplify(keep_shapes = T, sys = T) %>%
+  st_make_valid() %>%
+  filter(iso3 %in% unique(rlm_eez_cb$iso3))
+
+conserving_nations <- rlm_eez_cb %>% 
+  select(iso3, realm) %>% 
+  distinct()
+
 # PROCESSING ############################################################################################
 
 # Get targets
@@ -45,20 +60,22 @@ rlm_trading_prices <- rlm_h_sum %>%
   left_join(rlm_conservation_target, by = "realm") %>% 
   mutate(trading_price = map2_dbl(.x = target, .y = data, get_trading_price)) %>% 
   select(-data)
-  
+
 ## Identify conserved patches
 # Get the most efficient trading price
 
 # Filter to keep only the protected places
 bau <- rlm_eez_cb %>% 
-  filter(pct <= 0.3) %>%                       # Keep the most efficient 30% of each country - realm
+  group_by(iso3, realm) %>% 
+  mutate(min_pct = min(pct, na.rm = T)) %>% 
+  ungroup() %>% 
+  filter(pct <= 0.3 | pct <= min_pct) %>%                       # Keep the most efficient 30% of each country - realm
   mutate(approach = "bau")
 
 mkt <- rlm_eez_cb %>% 
   left_join(rlm_trading_prices, by = c("realm")) %>%
   filter(mc <= trading_price) %>%              # Keep all patches in each country with a cost < trading price
-  mutate(approach = "mkt") %>% 
-  select(-c(trading_price,))
+  mutate(approach = "mkt")
 
 ## Calculate country-level summaries
 # For BAU
@@ -67,27 +84,38 @@ realized_bau_cb <- bau %>%
   summarize(bau_tb = sum(benefit, na.rm = T),
             bau_tc = sum(cost, na.rm = T),
             mc_stop = max(mc, na.rm = T),
-            bau_area = n()) %>% 
[…]

### 2021-03-16 scripts/04_analysis/08_all_segments_all_scenarios.R

@@ -49,14 +49,24 @@ sea_h_sum <- readRDS(
 
 
 get_global_market_gains <- function(eez_cb, r, trading_price) {
+  
+  # browser()
+  
+  conserving_nations <- eez_cb %>% 
+    select(iso3) %>% 
+    distinct()
+  
   bau <- eez_cb %>% 
-    filter(pct <= r) %>%                       # Keep the most efficient r% of each country - hemisphere
+    group_by(iso3) %>% 
+    mutate(min_pct = min(pct, na.rm = T)) %>% 
+    ungroup() %>% 
+    filter(pct <= r | pct <= min_pct) %>% # Keep the most efficient r% of each country - hemisphere
     mutate(approach = "bau") %>% 
     group_by(approach, iso3) %>% 
     summarize(bau_tb = sum(benefit, na.rm = T),
               bau_tc = sum(cost, na.rm = T),
               mc_stop = max(mc, na.rm = T),
-              bau_area = n(),
+              bau_area = n() * 2500,
               .groups = "drop_last") %>% 
     ungroup()
   
@@ -66,20 +76,30 @@ get_global_market_gains <- function(eez_cb, r, trading_price) {
     group_by(approach, iso3) %>% 
     summarize(mkt_tb = sum(benefit, na.rm = T),
               mkt_tc = sum(cost, na.rm = T),
-              mkt_area = n(),
+              mkt_area = n() * 2500,
               .groups = "drop_last") %>% 
     ungroup()
   
+  combined_outcomes <- conserving_nations %>% 
+    left_join(mkt, by = "iso3") %>%
+    left_join(bau, by = "iso3") %>% 
+    replace_na(replace = list(
+      mkt_tb = 0, mkt_tc = 0, mkt_area = 0,
+      bau_tb = 0, bau_tc = 0, bau_area = 0)) %>% 
+    select(-contains("app")) %>% 
+    mutate(mkt_tc2 = mkt_tc + ((bau_tb - mkt_tb) * trading_price),
+           mkt_tc = ifelse(mkt_tc2 <=0, bau_tc, mkt_tc2)) %>% 
+    select(-mkt_tc2)
   
-  gains_from_trade <- full_join(mkt, bau, by = c("iso3"))  %>% 
-    select(contains("mkt"), contains("bau")) %>% 
+  gains_from_trade <- combined_outcomes %>% 
+    select_if(is.numeric) %>% 
     select(-contains("stop")) %>% 
     summarize_all(sum, na.rm = T) %>% 
-    ungroup() %>% 
[…]

### 2021-03-16 scripts/04_analysis/05_realm_level_market.R
changes

@@ -176,6 +176,16 @@ market_gains_plot <- combined_outcomes %>%
   scale_x_discrete(labels = c("BAU", "Market")) +
   coord_flip()
 
+
+ggplot(gains_from_trade, aes(x = variable, y = value, fill = approach)) +
+  geom_col(position = "dodge", color = "black") +
+  facet_grid(realm~variable, scale = "free") +
+  scale_fill_brewer(palette = "Set1", guide = F) +
+  ggtheme_plot() +
+  labs(x = "Approach", y = "Value") +
+  scale_x_discrete(labels = c("BAU", "Market")) +
+  coord_flip()
+
 map_contrasting_scenarios <- ggplot() +
   geom_sf(data = filter(eez_with_results,!variable == "gets_paid", str_detect(realm, "Atlantic")),
           aes(fill = value), color = "black") +
@@ -217,6 +227,11 @@ two_states_map <-
 
 
 ## EXPORT FIGURES #########################################################################
+
+lazy_ggsave(plot = market_gains_plot,
+            filename = "market_gains_plot_rlm",
+            width = 15,
+            height = 20)
 
 lazy_ggsave(plot = benefit_supply_curves,
             filename = "equilibrum_supply_curves_rlm",

### 2021-04-14 draft.Rmd
Added very vry rough draft
pdated draft with random sentences

@@
 
+It is important that we acknowledge the equity concerns of any conservation intenrvention.
+Under the current approach to conservation, nations face two options: to conserve 30% in situ, or not engage in conservation at all.
+This market-based approach allows for a third option: it allows nations to decide how much to conserve in their waters.
+
+Ocean grabbing, the term that relates to the loss of soveraignty in the ocean (see Benett) may be perceived as a problem.
+However, nations are not forced to conserve in situ, and will only do so if they are approrpiately compensated for it.
+
+All ecosystems are euqlly important for the subsistance of nature and species that reside in them.
+But a coral reef is not comparable to a kelp forest.
+A market design that doesn't acknowledge these differences may unintendendly bias conservation towards different ecosystems or geographic regions.
+When outcomes of a market are restricted to a geographic extent, such as air pollution markets, a buble policy is implemented.
+We borrow from this principle and use biogeographic regionalization principles to create ecologically-coherent market segments where nations trade similar habitat.
+For example, in the temperate eastern pacific, Mexico and the US will trade a same type of habitat, while in the Tropical Atlantic they wil.
+
+Having tackled these three limitations (spatially-independent measure, x, and market bubbles), we proceed to simulate the trade outcomes of such a market.
+We evaluate the outcomes across a range of target coverages (1 - 100), and find that a market always results in reduced costs.
+The absolute and relative magnitude of the costs-savings changes with protection target, peaking at between X and Y, depending on of the choice market segmentation.
+Intuitively, increasing teh number of market segments reduces the opportunity for bargaining and reduces the gains from trade, but ensures the persistance of different habitats.
+
+We pay especial attention to goals of interest, such as protecting 30% of the marine area (habitat suitability-weighted) within all national jurisdictions.
+We find that a market-based approach to conservation would reduce costs by X%, and that Y% less area would be needed.
+
 # Introduction
@@
 Finally, we discuss how the analysis can be replicated by creating markets at different spatial scales.
-
-## Data description
-
-We must first identify the costs and benefits of conservation.
-Conserving biodiversity may provide benefits to society.
-For example, areas with higher species richness and biomass are more attractive to tourism \citep{williams_2000}.
-Species richness also leads to increased stability of ecosystems \citep{tilman_1995}, and may reduce exposure to pathogens \citep{lamb_2017}.
-The quantification is not straightforward, but we can assume that biodiversity indices are positively correlated with their benefits they provide (although saturation may occur past a given point).
-
-I use spatially-explicit data on biodiversity benefit for each 50 X 50 km grid in the ocean.
-The score was derived to account for species richness and evolutionary distinctiveness, but also presence of topographic features (*e.g.* sea mounts).
-Figure \ref{fig:biodiversity-ranking} shows a global map of these values.
-The value of a given pixel (termed $\Delta v$) depends on previously protected pixels.
-As such, the value of a randomly chosen pixel is more or less meaningless.
-However, the configuration represented in Figure \ref{fig:biodiversity-ranking} was derived to maximize biodiversity.
-Therefore, protecting the best $n$ pixels and summing their values does represent the total amount of biodiversity protected.
-The same exercise has been done at the country-level (This is an important consideration for target calculations mentioned below.
-While I will use this global data for the purposes of motivating my approach, I do plan on using the appropriate data in my final work.)
-
-![\label{fig:biodiversity-ranking} Global map of biodiversity ranking priorities. Higher values indicate higher priority to conserve.](results/img/benefit_map.png)
-
-On the other hand, we need to quantify the costs associated to each pixel.
-An often-cited cost of implementing MPAs is that of losses in fisheries revenues \citep{smith_2010}.
-In this case, we define costs as losses in fisheries landings ^[I intend to use losses in fisheries revenues in the future.
-This will involve species-level changes in landings, as well as species-level price data.
-Essentially, the global losses in landings used here will be weighed by species price data.].
-Since protection of some areas may lead to rebuilding fisheries, parts of the ocean might have negative costs.
-This means that there are gains to be made in conserving them.
-A map of global costs of conservation is shown in Figure \ref{fig:landing-losses}.
-As before, these data do not consider the transient dynamics, and represent the equilibrium state of protecting any given pixel.
-
-![\label{fig:landing-losses} Global map showing the costs (losses in landings) from closing portions of the ocean. Negative values imply that there are gains to be made.](results/img/cost_map.png)
-
-\FloatBarrier
-
-## Building supply curves
-
-Although there are important caveats, these data provide us with a way of calculating the costs and benefits of protecting any place under a nation's jurisdiction.
-While protecting the high seas may provide many benefits \citep{white_2014, sumaila_2015}, our market-based approach requires enforceable property rights, such as those offered by Exclusive Economic Zones.
-Moreover, biodiversity benefit is higher within Exclusive Economic Zones, where most of the species live \citep{mayorga_2020}.
-Therefore, we will ignore areas beyond national jurisdiction.
-
-The next step is to identify which areas to protect.
-For two grid cells that provide equal biodiversity benefit, which one should be prioritized?
-This prioritization exercise need not be too complicated.
-We can assume that even if a country is seriously committed to conservation, costs must still be minimized.
-The most efficient thing to do is to protect the one that minimizes costs while maximizing biodiversity benefits.
-Therefore, we must calculate the benefit-cost ratio of each gridcell:
-
-$$
-BCR_i = \frac{B_i}{C_i}
-$$
-
-Where $B_i$ corresponds to the biodiversity benefit associated with protecting cell $i$, and $C_i$ corresponds to the costs of protecting cell $i$.
-We can do this calculation globally, and produce a map of BCR (Figure \ref{fig:bcr-map}).
-Due to the possibility of negative costs, the BCR may be negative.
-We must therefore differentiate the BCR of cells with negative and positive costs, and rank them in this nested way.
-
-![\label{fig:bcr-map} Map of Benefit-Cost Ratio (BCR) within nation's Exclusive Economic Zones.](results/img/bcr_map.png)
-
-For each country, we can rank the grid cells by their BCR and calculate the total biodiversity benefit and total costs of achieving that benefit.
-But more importantly, we can calculate the marginal costs (defined as the cost of protecting an extra unit of biodiversity: tonnes of fish lost / benefit unit), and produce a supply curve of conservation for each country.
-Their shape suggests that the first few units of conservation can be achieved at relatively low costs, but that it becomes increasingly costly to obtain more and more biodiversity benefits.
-Figure \ref{fig:eez-supply-curve} shows the biodiversity supply curves of each country, and the horizontally-summed global supply curve.
-
-![\label{fig:eez-supply-curve}Supply curve for each country](results/img/eez_supply_curve.png)
-
-## Finding targets and trading price
-
-<!-- MAYBE:: A meta-analysis of simulation studies suggests that targets ranging from biodiversity protection to food provisioning can be indeed achieved by protecting ~30% of our coastal oceans \citep{oleary_2016,cabral_2019}.
-However, these area-based targets ultimately imply a desired level of biodiversity benefit.
--->
-
-The supply curves above will tell us the per-unit-costs of achieving a given amount of biodiversity benefit.
-But what is this "desired" amount of biodiversity benefit?
-All conservation targets are area-based, and do not explicitly call for an amount of conservation such as "protect 20 species", or "protect 3 habitats".
-However, we know the costs and benefits of each grid cell.
-This allows us to anticipate how rational nations may translate their area-based requirements into conservation interventions.
-
-Figure \ref{fig:eez-supply-curve-approaches} shows five possible ways in which nations may reach an area-based target.
-Each panel shows the amount of biodiversity benefit produced by protecting a given percentage (x-axis) of a nation's EEZ.
-The only difference between panels is the strategy taken by nations, which leads to different curvatures.
-In the first panel, labeled as "efficient", nations conserve area in decreasing BCR values.
-The second panel maximizes conservation, and nations protect based on the biodiversity benefit rankings and completely ignore the costs.
-Similarly, the third panel seeks to maximize costs only, without accounting for how much conservation is achieved.
-The last two panels do the opposite, and try to minimize conservation or costs, without accounting for the other.
-The scenarios where costs are maximized or biodiversity benefits minimized are of course unlikely, however they provide bounds for where the true target lies.
-From now on, we will move forward with he efficient target of achieving 72 units of biodiversity benefit.
-
-The most efficient way to achieve this level of conservation is by prioritizing places with a higher BCR.
-We can take the horizontally-summed global supply curve of biodiversity and find the corresponding costs for each of the benefit targets identified above (Figure \ref{fig:global-conservation-targets-and-trading-prices}).
-This values are also known as the trading price.
-A nation will continue to conserve in-situ up until the cost of an additional unit of conservation is equal to this value.
-Instead, it is more cost-effective to conserve elsewhere in the world where the costs are lower.
 
@@
 
+# Supplementary Information
+
+## Data description
+
+We must first identify the costs and benefits of conservation.
+Conserving biodiversity may provide benefits to society.
+For example, areas with higher species richness and biomass are more attractive to tourism \citep{williams_2000}.
+Species richness also leads to increased stability of ecosystems \citep{tilman_1995}, and may reduce exposure to pathogens \citep{lamb_2017}.
+The quantification is not straightforward, but we can assume that biodiversity indices are positively correlated with their benefits they provide (although saturation may occur past a given point).
+
+I use spatially-explicit data on biodiversity benefit for each 50 X 50 km grid in the ocean.
+The score was derived to account for species richness and evolutionary distinctiveness, but also presence of topographic features (*e.g.* sea mounts).
+Figure \ref{fig:biodiversity-ranking} shows a global map of these values.
+The value of a given pixel (termed $\Delta v$) depends on previously protected pixels.
+As such, the value of a randomly chosen pixel is more or less meaningless.
+However, the configuration represented in Figure \ref{fig:biodiversity-ranking} was derived to maximize biodiversity.
+Therefore, protecting the best $n$ pixels and summing their values does represent the total amount of biodiversity protected.
+The same exercise has been done at the country-level (This is an important consideration for target calculations mentioned below.
+While I will use this global data for the purposes of motivating my approach, I do plan on using the appropriate data in my final work.)
+
+![\label{fig:biodiversity-ranking} Global map of biodiversity ranking priorities. Higher values indicate higher priority to conserve.](results/img/benefit_map.png)
+
+On the other hand, we need to quantify the costs associated to each pixel.
+An often-cited cost of implementing MPAs is that of losses in fisheries revenues \citep{smith_2010}.
+In this case, we define costs as losses in fisheries landings ^[I intend to use losses in fisheries revenues in the future.
+This will involve species-level changes in landings, as well as species-level price data.
+Essentially, the global losses in landings used here will be weighed by species price data.].
+Since protection of some areas may lead to rebuilding fisheries, parts of the ocean might have negative costs.
+This means that there are gains to be made in conserving them.
+A map of global costs of conservation is shown in Figure \ref{fig:landing-losses}.
+As before, these data do not consider the transient dynamics, and represent the equilibrium state of protecting any given pixel.
+
+![\label{fig:landing-losses} Global map showing the costs (losses in landings) from closing portions of the ocean. Negative values imply that there are gains to be made.](results/img/cost_map.png)
+
+\FloatBarrier
+
+## Building supply curves
+
+Although there are important caveats, these data provide us with a way of calculating the costs and benefits of protecting any place under a nation's jurisdiction.
+While protecting the high seas may provide many benefits \citep{white_2014, sumaila_2015}, our market-based approach requires enforceable property rights, such as those offered by Exclusive Economic Zones.
+Moreover, biodiversity benefit is higher within Exclusive Economic Zones, where most of the species live \citep{mayorga_2020}.
+Therefore, we will ignore areas beyond national jurisdiction.
+
+The next step is to identify which areas to protect.
+For two grid cells that provide equal biodiversity benefit, which one should be prioritized?
+This prioritization exercise need not be too complicated.
+We can assume that even if a country is seriously committed to conservation, costs must still be minimized.
+The most efficient thing to do is to protect the one that minimizes costs while maximizing biodiversity benefits.
+Therefore, we must calculate the benefit-cost ratio of each gridcell:
+
+$$
+BCR_i = \frac{B_i}{C_i}
+$$
+
+Where $B_i$ corresponds to the biodiversity benefit associated with protecting cell $i$, and $C_i$ corresponds to the costs of protecting cell $i$.
+We can do this calculation globally, and produce a map of BCR (Figure \ref{fig:bcr-map}).
+Due to the possibility of negative costs, the BCR may be negative.
+We must therefore differentiate the BCR of cells with negative and positive costs, and rank them in this nested way.
+
+![\label{fig:bcr-map} Map of Benefit-Cost Ratio (BCR) within nation's Exclusive Economic Zones.](results/img/bcr_map.png)
+
+For each country, we can rank the grid cells by their BCR and calculate the total biodiversity benefit and total costs of achieving that benefit.
+But more importantly, we can calculate the marginal costs (defined as the cost of protecting an extra unit of biodiversity: tonnes of fish lost / benefit unit), and produce a supply curve of conservation for each country.
+Their shape suggests that the first few units of conservation can be achieved at relatively low costs, but that it becomes increasingly costly to obtain more and more biodiversity benefits.
+Figure \ref{fig:eez-supply-curve} shows the biodiversity supply curves of each country, and the horizontally-summed global supply curve.
+
+![\label{fig:eez-supply-curve}Supply curve for each country](results/img/eez_supply_curve.png)
+
+## Finding targets and trading price
+
+<!-- MAYBE:: A meta-analysis of simulation studies suggests that targets ranging from biodiversity protection to food provisioning can be indeed achieved by protecting ~30% of our coastal oceans \citep{oleary_2016,cabral_2019}.
+However, these area-based targets ultimately imply a desired level of biodiversity benefit.
+-->
+
+The supply curves above will tell us the per-unit-costs of achieving a given amount of biodiversity benefit.
+But what is this "desired" amount of biodiversity benefit?
+All conservation targets are area-based, and do not explicitly call for an amount of conservation such as "protect 20 species", or "protect 3 habitats".
+However, we know the costs and benefits of each grid cell.
+This allows us to anticipate how rational nations may translate their area-based requirements into conservation interventions.
+
+Figure \ref{fig:eez-supply-curve-approaches} shows five possible ways in which nations may reach an area-based target.
+Each panel shows the amount of biodiversity benefit produced by protecting a given percentage (x-axis) of a nation's EEZ.
+The only difference between panels is the strategy taken by nations, which leads to different curvatures.
+In the first panel, labeled as "efficient", nations conserve area in decreasing BCR values.
+The second panel maximizes conservation, and nations protect based on the biodiversity benefit rankings and completely ignore the costs.
+Similarly, the third panel seeks to maximize costs only, without accounting for how much conservation is achieved.
+The last two panels do the opposite, and try to minimize conservation or costs, without accounting for the other.
+The scenarios where costs are maximized or biodiversity benefits minimized are of course unlikely, however they provide bounds for where the true target lies.
+From now on, we will move forward with he efficient target of achieving 72 units of biodiversity benefit.
+
+The most efficient way to achieve this level of conservation is by prioritizing places with a higher BCR.
+We can take the horizontally-summed global supply curve of biodiversity and find the corresponding costs for each of the benefit targets identified above (Figure \ref{fig:global-conservation-targets-and-trading-prices}).
+This values are also known as the trading price.
+A nation will continue to conserve in-situ up until the cost of an additional unit of conservation is equal to this value.
+Instead, it is more cost-effective to conserve elsewhere in the world where the costs are lower.
+
 \bibliography{references}

### 2021-06-15 draft.Rmd
Updated intro and part of methods, added references

@@
     institute: bren
-  - name: Juan Mayorga
+  - name: Juan S. Mayorga-Henao
     institute: bren
@@
       - '--lua-filter=author-info-blocks.lua'
+biblio-style: "nature"
 header-includes:
@@
 
-# Important sentences
+<!-- # Important sentences -->
 
-Importantly, the quality of a patch can be defined independently of other pixels.
+<!-- Importantly, the quality of a patch can be defined independently of other pixels.
 This is true for habitat suitability, in which the abiotic characteristics that determine the suitability of a patch are independent of the protected status of any patch.
+-->
 
-It is important that we acknowledge the equity concerns of any conservation intenrvention.
+<!-- It is important that we acknowledge the equity concerns of any conservation intenrvention.
 Under the current approach to conservation, nations face two options: to conserve 30% in situ, or not engage in conservation at all.
 This market-based approach allows for a third option: it allows nations to decide how much to conserve in their waters.
+-->
 
-Ocean grabbing, the term that relates to the loss of soveraignty in the ocean (see Benett) may be perceived as a problem.
+<!-- Ocean grabbing, the term that relates to the loss of soveraignty in the ocean (see Benett) may be perceived as a problem.
 However, nations are not forced to conserve in situ, and will only do so if they are approrpiately compensated for it.
+-->
 
-All ecosystems are euqlly important for the subsistance of nature and species that reside in them.
+<!-- All ecosystems are euqlly important for the subsistance of nature and species that reside in them.
 But a coral reef is not comparable to a kelp forest.
@@
 For example, in the temperate eastern pacific, Mexico and the US will trade a same type of habitat, while in the Tropical Atlantic they wil.
+-->
 
-Having tackled these three limitations (spatially-independent measure, x, and market bubbles), we proceed to simulate the trade outcomes of such a market.
+<!-- Having tackled these three limitations (spatially-independent measure, x, and market bubbles), we proceed to simulate the trade outcomes of such a market.
 We evaluate the outcomes across a range of target coverages (1 - 100), and find that a market always results in reduced costs.
@@
 Intuitively, increasing teh number of market segments reduces the opportunity for bargaining and reduces the gains from trade, but ensures the persistance of different habitats.
+-->
 
-We pay especial attention to goals of interest, such as protecting 30% of the marine area (habitat suitability-weighted) within all national jurisdictions.
+<!-- We pay especial attention to goals of interest, such as protecting 30% of the marine area (habitat suitability-weighted) within all national jurisdictions.
 We find that a market-based approach to conservation would reduce costs by X%, and that Y% less area would be needed.
+-->
 
-# Introduction
+# Main
 
-Nations have committed to protect a fixed portion of their EEZs in order to reduce and control anthropogenic impacts in the marine environment.
-Aichi target 11^[Aichi target 11 states that by 2020 10% of coastal and marine areas should be conserved through protected areas.] and target 14.5 of the United Nations Sustainable Development Goals^[Similarly, target 14.5 of the United Nations Sustainable Development Goals is to conserve at least 10% of coastal and marine areas.] aim to protect 10% of coastal and marine areas.
-Some more ambitious goals call for 30%, such as that from the World Parks Congress^[the International Union for the Conservation of Nature (IUCN) has suggested that at least 30% of each marine habitat should be protected in areas with no extractive activities.].
+More than three decades of conservation science have shown us that well-designed Marine Protected Areas (MPAs) can deliver large economic and ecological benefits\cite{halpern_2008,cabral_2019, cabral_2020}.
+Various international goals seek to protect anywhere between 10\% and 30\% of the global ocean with MPAs.
+Along with these commitments, the scientific roadmap on where to site them\cite{roberts_2002,worm_2003,lucifora_2011,wallace_2011,albouy_2017,sala_2021} should be enough to see these goals realized.
+Why, then, have some nations achieved (and even surpassed) the ambitious 30\% target, while others lag behind even the modest 10\% target?
+Partly, because under the current unilateral conservation framework some nations face higher costs of conservation than others.
+Here, we show how an environmental market can be designed to lower the costs of conservation and induce cooperation towards a more efficient and equitable protection of the marine environment.
 
-These goals ultimately aim to protect a global amount of biodiversity by spatially abating risks.
-However, costs and benefits are heterogeneous in space, and even conservation-minded countries might struggle to meet these targets if costs are prohibitive.
-But what if a nation could pay to conserve elsewhere, where the costs are lower?
-This setup is similar to that of pollution abatement in a multi-firm setting.
-A large body of theoretical and empirical literature has shown that an efficient way to achieve a level of pollution abatement is by leveraging differences in firm's marginal cost curves and incentivizing trade of emission permits.
+Habitat suitability, and the costs of protecting it, are heterogeneously distributed across the globe and non-perfectly correlated \cite{halpern_2008,roberts_2002,kroodsma_2018}.
+As a result, different nations can attain the same amount of conservation for dramatically different costs, questioning the efficiency and equity of the current unilateral approach to marine conservation.
+But what if there were a way to maximize global conservation while lowering national costs of conserving?
+We propose a new institution where nations facing large costs of conserving in their Exclusive Economic Zones (EEZ) can purchase conservation credits from nations with a surplus of habitat worth protecting, and show that the costs of conservation can be dramatically reduced.
 
-Just as any two firms are capable of reducing their emissions by a given amount, two nations are capable of implementing MPAs with the same biodiversity value.
-However one nation (or firm) may be able to do so at a lower cost.
-A market approach may be the most efficient (*i.e.* cost-effective) way of balancing these differences in costs and benefits, and ultimately allow us to reach the desired targets at a reduced cost.
+The latest findings on marine conservation prioritization  show that a globally coordinated effort is more efficient than unilateral conservation efforts\cite{sala_2021}.
+While these results can point out where protection is most warranted and highlight the importance of coordination, they do little to incentivize nations to engage in it.
+Instead, institutions are needed to align actions with the desired conservation outcomes.
+One way to induce this desired cooperation is by allowing nations to conserve *in situ* (\emph{i.e.} within their EEZ) or pay to conserve *ex situ* (\emph{i.e.} in another nation's EEZ) to meet an aggregate target.
 
-Under such a market, what would be the gains from trade?
-For the same amount of conservation as in the BAU scenario, how much are the costs reduced?
-How does spatially dividing the market (say, by ecosystem or ocean) change the outcome?
-This are indeed the questions that I seek to answer.
+A market for conservation credits would allow just that.
+However, in designing such a market, two main challenges arise.
+First, not all ecosystems are created equally.
+Protecting one hectare of coral reef is not the same as protecting one hectare of kelp forest.
+A conservation market that ignores this could inadvertently fail to protect important habitat.
+Secondly, we live in a highly dynamic and connected world, one in which the biodiversity and costs of a patch of ocean depend on what else has been (or will be) protected, as well as it's own protection status.
+We provide solutions to both of these problems, and then simulate the trade outcomes of a global market for marine conservation credits and compare them to the business-as-usual baseline of unilateral conservation.
+For a range MPA coverage targets (1\% - 99\%), we find that a market always reduces the cost of conservation, resulting in a more efficient and equitable outcome.
 
-# Methods
+# Designing a market for conservation credits
 
-We combine data on biodiversity benefit and costs to generate supply curves for each nation, as well as a global biodiversity supply curve.
+The first challenge in designing a market for conservation credits is to ensure that all ecosystems are properly protected.
+A coral reef can not be substituted for a kelp forest - they complement each other to produce our world's rich biodiversity.
+One way to avoid trading credits across different ecosystems is by using a "bubble policy" \cite{fr_1979}.
+In air quality management, this approach enables polluting plants to flexibly manage their air emissions.
+By placing a “bubble” over a city with multiple polluting plants and applying a single emission cap to the “bubbled” city, each plant can decide how to internally manage production and trade emissions permits accordingly.
+
+We use biogeographic regionalization (Realms and Provinces \cite{spalding_2007} Fig S1) to create ecologically-coherent "blue bubbles" where nations trade conservation credits for similar habitats.
+For example, for Realm-based bubbles, Mexico and the United States trade conservation credits under two blue bubbles (Temperate Eastern Pacific [TEP] and Tropcial Atlantic [TA]), using bubble-specific conservation credits (\emph{e.g.} Kelp forest in the TEP and coral reefs in the TA).
+
+The second challenge a market faces is in the deffinition of conservation targets.
+In the air pollution example, the target can be a fixed amount or ambient concentration of a pollutant, both of which are measurable quantities.
+Moreover, the amount of pollution in one bubble is not affected by the management status of the adjacent bubbles.
+However, biodiversity is an elusive variable, with multiple nuanced indices implicitly assigning weighs to different features (\emph{e.g.} species richness does not weigh abundance, while biomass does not acount for richness).
+Moreover, the biodiversity for any pixel in the world will be influenced by the protection status of itself, but also the network of connected pixels.
+
+Instead, we define the value of a pixel based on its surface area and the suitability of the habitat it contains for the species distributed there.
+Habitat suitability is defined as X.
+Conveniently, the habitat suitability of any pixel in the ocean can be defined independently of the habitat suitability and protection status of other pixels.
+Habitat suitability maps for 4,000 (exact number here) marine species, as indicated by the probability of occurrence which is a function of X, Y and Z \cite{ready_2010}.
+The habitat suitability of any pixel in the world can be calculated as the average suitability across all species, conditional on the pixel being suitable (i.e.
+p > 0.5).
+
+Marine Protected Areas are spatial conservation interventions that seek to directly protect habitat and, indirectly, the species that reside there.
+The siting of MPAs can therefore be guided by abiotic characteristics that are conducive to the persistence of species.
+Together, these abiotic characteristics define the habitat suitability of a patch for a given species.
+
+# Simulations
+
+We combine habitat suitability and fisheries revenue to generate supply curves for each nation, as well as a global biodiversity supply curve.
 While in practice this approach can be used for any given biodiversity target, I produce an example using the 30% area-based target (*i.e.* We translate this area-based target into biodiversity units).
@@
 Here, we use different scales of zoning in the marine environment (*i.e.* Biogeographic zoning).
-\citet{spalding_2007} divided the oceans using a hierarchical approach with Realms (n = 12) containing Provinces (n = 60), which in turn contain Ecoregions (n = 219).
+\cite{spalding_2007} divided the oceans using a hierarchical approach with Realms (n = 12) containing Provinces (n = 60), which in turn contain Ecoregions (n = 219).
 
@@
 
-![\label{fig:realm-map}Map of the 12 realms, as defined by \citet{spalding_2007}.](results/img/realm_map.png)
-
-![\label{fig:eezs-per-realm} Number of nations contained within each of the realms described by \citet{spalding_2007}.
+![\label{fig:eezs-per-realm} Number of nations contained within each of the realms described by \cite{spalding_2007}.
 The vertical dashed line lies at 2,  the minimum number of nations required for trade to occur.](results/img/eezs_per_realm.png)
@@
 
+![\label{fig:realm-map}Map of the 12 realms, as defined by \cite{spalding_2007}.](results/img/realm_map.png)
+
+Map of provinces
+
 ## Data description
@@
 Conserving biodiversity may provide benefits to society.
-For example, areas with higher species richness and biomass are more attractive to tourism \citep{williams_2000}.
-Species richness also leads to increased stability of ecosystems \citep{tilman_1995}, and may reduce exposure to pathogens \citep{lamb_2017}.
+For example, areas with higher species richness and biomass are more attractive to tourism \cite{williams_2000}.
+Species richness also leads to increased stability of ecosystems \cite{tilman_1995}, and may reduce exposure to pathogens \cite{lamb_2017}.
 The quantification is not straightforward, but we can assume that biodiversity indices are positively correlated with their benefits they provide (although saturation may occur past a given point).
@@
 On the other hand, we need to quantify the costs associated to each pixel.
-An often-cited cost of implementing MPAs is that of losses in fisheries revenues \citep{smith_2010}.
+An often-cited cost of implementing MPAs is that of losses in fisheries revenues \cite{smith_2010}.
 In this case, we define costs as losses in fisheries landings ^[I intend to use losses in fisheries revenues in the future.
@@
 Although there are important caveats, these data provide us with a way of calculating the costs and benefits of protecting any place under a nation's jurisdiction.
-While protecting the high seas may provide many benefits \citep{white_2014, sumaila_2015}, our market-based approach requires enforceable property rights, such as those offered by Exclusive Economic Zones.
-Moreover, biodiversity benefit is higher within Exclusive Economic Zones, where most of the species live \citep{mayorga_2020}.
+While protecting the high seas may provide many benefits \cite{white_2014, sumaila_2015}, our market-based approach requires enforceable property rights, such as those offered by Exclusive Economic Zones.
+Moreover, biodiversity benefit is higher within Exclusive Economic Zones, where most of the species live \cite{sala_2021}.
 Therefore, we will ignore areas beyond national jurisdiction.
@@
 
-<!-- MAYBE:: A meta-analysis of simulation studies suggests that targets ranging from biodiversity protection to food provisioning can be indeed achieved by protecting ~30% of our coastal oceans \citep{oleary_2016,cabral_2019}.
+<!-- MAYBE:: A meta-analysis of simulation studies suggests that targets ranging from biodiversity protection to food provisioning can be indeed achieved by protecting ~30% of our coastal oceans \cite{oleary_2016,cabral_2019}.
 However, these area-based targets ultimately imply a desired level of biodiversity benefit.

### 2021-06-18 draft.Rmd
Updating draft

@@
   - name: Darcy Bradley
-    institute: bren
+    institute: bren, emlab
   - name: Christopher Costello
-    institute: bren
+    institute: bren, emlab, econ
   - name: Juan S. Mayorga-Henao
-    institute: bren
+    institute: bren, emlab
   - name: Andrew Plantinga
-    institute: bren
+    institute: bren, econ
 institute:
-  - bren: Bren School of Environmental Science and Management, University of California Santa Barbara
+  - bren: Bren School of Environmental Science & Management, University of California, Santa Barbara, Santa Barbara, CA, USA
+  - emlab: Environmental Market Solutions Lab, University of California, Santa Barbara, Santa Barbara, CA, USA
+  - econ: Department of Economics, University of California, Santa Barbara, Santa Barbara, CA, USA
 date: "Prepared on `r format(Sys.time(), '%B %d, %Y')`"
-abstract: "Humanity depends on the ocean for livelihood, subsitance, and way of life.
-Yet, many of our activities continiously pose a threat to marine populations and ecosystems.
-The implementation of Marine Protected Areas (MPAs), where extractive activities are regulated or prohibited on the basis of spatial deliniations, are one of many ways to manage the oceans.
-Current intenrational agreements call to achieve a certain amount of within-country conservation.
-Here we explore the benefits from implementing a market for conservation in which nations trade conservation towards a global target.
-We find that such a market reduces the costs of conservation by 46%, relative to a BAU scenario without a market where each country protects a fixed portion of their waters.
-When creating 12 distinct markets based on biogeography regionalization, we find that costs are reduced by 34.8%."
+abstract: "Freewriteplaceholder, not actually an abstract: Can environmental markets be designed to induce global cooperation towards conservation of the marine environment?
+We propose a new institution where nations facing large costs of conserving in their waters can purchase conservation credits from nations with a surplus of habitat to protect.
+We will build a spatially-explicit bio-economic model of trade and conservation, and leverage high-resolution spatial data and state-of-the-art computation modeling to simulate the conservation and cost-reduction outcomes of cooperation.
+We derive the conditions uner which a market can produce gains, and show how the design features can incentivize meaningful conservation.
+We find that a market alwaysr educes teh costs of conservation."
 fontsize: 12pt
@@
 
-Habitat suitability, and the costs of protecting it, are heterogeneously distributed across the globe and non-perfectly correlated \cite{halpern_2008,roberts_2002,kroodsma_2018}.
+Habitat suitability, and the costs of protecting it, are heterogeneously distributed across the globe \cite{halpern_2008,roberts_2002,kroodsma_2018}.
 As a result, different nations can attain the same amount of conservation for dramatically different costs, questioning the efficiency and equity of the current unilateral approach to marine conservation.
@@
 
-The latest findings on marine conservation prioritization  show that a globally coordinated effort is more efficient than unilateral conservation efforts\cite{sala_2021}.
-While these results can point out where protection is most warranted and highlight the importance of coordination, they do little to incentivize nations to engage in it.
-Instead, institutions are needed to align actions with the desired conservation outcomes.
-One way to induce this desired cooperation is by allowing nations to conserve *in situ* (\emph{i.e.} within their EEZ) or pay to conserve *ex situ* (\emph{i.e.} in another nation's EEZ) to meet an aggregate target.
+The latest work on marine conservation prioritization shows that a globally coordinated effort to conserve the ocean is more efficient than unilateral conservation efforts\cite{sala_2021}.
+While these results highlight the importance of coordination and identify where protection is warranted, they are not enough to incentivize nations.
+But how can we induce cooperation on globa marine conservation?
+One way to induce this desired cooperation is by giving nations the option to meet their conservation targets *in situ* (\emph{i.e.} within their EEZ) or pay to conserve *ex situ* (\emph{i.e.} in another nation's EEZ, who have a surpluss of area to conserve).
 
@@
 
+# Spatial heterogeneity
+
+The motivation from a market-based approach to conservation relies on two premises.
+First, that habitat worth protecting is heterogeneously distributed across nations.
+And, secondly, that the costs of protecting habitat are non-perfectly correlated with the protection value of the pixel.
+Together, these two features make it possible to lower costs by using trade to protect the most cost-effective places.
+The magnitude of market gains (that is, cost savings relative to BAU unilateral conservation with no trade) will depend on the correlation between costs and benefits.
+To illustrate this point, we generate synthetic data to simulate 20 girded worlds where the conservation value of a pixel is heterogeneously distributed, and where costs and benefits exhibit varying degrees of correlation (R from -1 to 1; See methods for a detailed description on synthetic data generation).
+For each scenario, we calculate the gains from trade for a series of protection targets (1 - 100%).
+We find that unless the costs and benefits are perfectly correlated (\emph{i.e.} R = 1), a market will always lower the costs of conservation for any desired target.
+
 # Designing a market for conservation credits
 
+Unlike the synthetic world described above, our planet contains a diverse array of different ecosystems, all of which are worth protecting.
 The first challenge in designing a market for conservation credits is to ensure that all ecosystems are properly protected.
-A coral reef can not be substituted for a kelp forest - they complement each other to produce our world's rich biodiversity.
-One way to avoid trading credits across different ecosystems is by using a "bubble policy" \cite{fr_1979}.
-In air quality management, this approach enables polluting plants to flexibly manage their air emissions.
+A colorful coral reef can not be substituted for a productive kelp forest - they complement each other to produce our world's rich biodiversity.
+How then, do we ensure that a market does not bias protection to one ecosystem or the other?
+A potential solution is to use a "bubble policy" \cite{fr_1979}.
+First introduced in air quality management, this approach enables polluting plants to flexibly manage their air emissions.
 By placing a “bubble” over a city with multiple polluting plants and applying a single emission cap to the “bubbled” city, each plant can decide how to internally manage production and trade emissions permits accordingly.
@@
 
-The second challenge a market faces is in the deffinition of conservation targets.
-In the air pollution example, the target can be a fixed amount or ambient concentration of a pollutant, both of which are measurable quantities.
-Moreover, the amount of pollution in one bubble is not affected by the management status of the adjacent bubbles.
-However, biodiversity is an elusive variable, with multiple nuanced indices implicitly assigning weighs to different features (\emph{e.g.} species richness does not weigh abundance, while biomass does not acount for richness).
-Moreover, the biodiversity for any pixel in the world will be influenced by the protection status of itself, but also the network of connected pixels.
+The second challenge a market faces is defining conservation targets.
+In the air quality example, the target can easily be set to be an amount (\emph{e.g.} tons of CO2) or ambient concentration (\emph{e.g.} ppm) of a pollutant, both of which are measurable quantities.
+An important feature is that the amount of pollution in one bubble can be determined independently of the management and amounts of pollution in adjacent bubbles.
+However, biodiversity is an elusive variable with multiple nuanced indices that implicitly assign weighs to different features (\emph{e.g.} species richness ignores abundance, while biomass ignores richness).
+Moreover, the biodiversity for any pixel in the world will be influenced by the protection status of said pixel, but also the network of connected pixels.
+The network of MPAs required to contain 100 species may not nessesarily be a subset of the network required to protect 101 species.
 
-Instead, we define the value of a pixel based on its surface area and the suitability of the habitat it contains for the species distributed there.
-Habitat suitability is defined as X.
-Conveniently, the habitat suitability of any pixel in the ocean can be defined independently of the habitat suitability and protection status of other pixels.
-Habitat suitability maps for 4,000 (exact number here) marine species, as indicated by the probability of occurrence which is a function of X, Y and Z \cite{ready_2010}.
-The habitat suitability of any pixel in the world can be calculated as the average suitability across all species, conditional on the pixel being suitable (i.e.
-p > 0.5).
+To work around this problem, we define the value of a pixel based on its surface area and the suitability of the habitat it contains for the species distributed there.
+Habitat suitability is defined as the joint probability of encountering a species, conditional on th abiotic characteristics of a pixel (\emph{e.g.} salinity, temperature, productivity, depth).
+We use habitat suitability maps for 4,000 **(exact number here)** marine species \cite{ready_2010} to calculate average suitability across all species.
+Conveniently, the habitat suitability of any pixel in the ocean can be defined independently of the habitat suitability and protection status of all other pixels.
+Moreover, Marine Protected Areas are spatial conservation interventions that seek to directly protect habitat and, indirectly, the species that reside there.
+The siting of MPAs can therefore be guided by abiotic characteristics that are conducive to the persistence of species.
 
-Marine Protected Areas are spatial conservation interventions that seek to directly protect habitat and, indirectly, the species that reside there.
-The siting of MPAs can therefore be guided by abiotic characteristics that are conducive to the persistence of species.
-Together, these abiotic characteristics define the habitat suitability of a patch for a given species.
+To provide a working example of a market for conservation credits, we must define costs.
+The real world is unlikely to exhibit perfect correlation between costs and benefits of conservation.
+We use spatially explicit data ob average fisheries revenue (2000 - 2015) \cite{melnychuk_2017,sumaila_2007,swartz_2013}.
+MPAs may certainly have positive impacts on fisheries revenue.
+Instead, our use of mean fisheries revenue should be interpreted as a proxy for the short-term political cost of displacing fishers, even if those same fishers might be better off in the future \cite{cabral_2020, cabral_2021}.
+In practice, the deffinition of costs will include other considerations, and may even vary from nation to nation.
+Special attention is given to this in our discussion section.
 
-# Simulations
+# Results
 
-We combine habitat suitability and fisheries revenue to generate supply curves for each nation, as well as a global biodiversity supply curve.
-While in practice this approach can be used for any given biodiversity target, I produce an example using the 30% area-based target (*i.e.* We translate this area-based target into biodiversity units).
-We then find the trading price in the global supply curve and use the country-level supply curves to calculate in-situ and ex-situ conservation for every country.
-We can then calculate the differences in costs, and estimate the gains from trade.
+We simulate with syntthetic data, and then provide an example of an operationalization of the concept.
+We present results for blue bubbles defined by biogeographic realms, but our suplementary materials present results for provinces, hemispheres, and oceans.
+We then focus our attention on the often-cited target of protecting 30% of the world.
+We show the directionality of trade (who pays to conserve and who gets paid to conserve), a comparision of area that would be protected under either or both scenarios.
+Lastly, we explore whether a realm-based market results in biased conservation for different taxa.
 
-The same approach can then be repeated for any level of spatial aggregation.
+Our simulation with synthetic data, where the correlations and distributions are known, shows that gains from trade are positive so long as costs and benefits are not perfectly correlated.
+Importantly, the gains from trade grow as spatial concordance decreases.
+This is an important insight, because it suggests that unless the real world exhibits perfect correlsation, there are potential gains frome trade.
+
+## Operationaling of a conservation credit market
+
+We combine habitat suitability and fisheries revenue to generate supply curves for each nation, with markets ipperating under five different bubble policies (global, hemisphere, realm, sea, and province).
+Since benefits and costs are not perfectly correlated (fig X with corr betwieen habitat suitability and fisheries revenue), we find that trade always results in cost-savings.
+Increasing the number of bubbles reduces market gains, because there is less opportunity for trade.
+Increasing the number of constraints often limits win-wins \cite{burgiuess_2021}.
+
+![\label{fig:all-segs-all-scen}All segmetns all scenarios.](results/img/gain_from_trade_segmented_market_plot.png)
+
+Each target protection level has a distinct market equilibrium.
+The following sections focus on the often-cited conservation target of protecting 30% of the oceans.
+For the purpose of the main text, we focus on the case where bubbles are defined by realms.
+We find that in every realm, there are at least two nations engaging in trade.
+This is important, because it shows that the results are not driven by trade ocurring in just one realm.
+The trading status of each nation in is shown globaly in figure \ref{fig:map-of-trade} and for each realm in figure \ref{fig:rlm-map-of-trade}.
+
+![\label{fig:map-of-trade}Map of trade.
+Blue indicates nations that reach the trading price before meeting their target, and therefore chose to pay to conserve elsewhere.
+Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/map_of_trade.png)
+
+![\label{fig:rlm-map-of-trade}Map of trade for each realm.
+Blue indicates nations that reach the trading price before meeting their target, and therefore chose to pay to conerve elsewhere.
+Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/rlm_map_of_trade.png)
+
+A pervasive finding on environmental markets is that market forces can lead to conglomeration of rights.
+In this case, this could be interpreted as one nation holding all effective conservation, or one nation not conserving at all.
+To test for conglomeration, we compare the MPA networks created by the market and BAU scenarios.
+Figure \ref{fig:two-states-map} shows the four possible categories for all pixels in the world: protected under BAU and market scenarios, protected only under BAU, protected only with a market, and not protected at all.
+We find no conglomeration.
+
+![\label{fig:two-states-map} Map of two possible conservation outcomes.](results/img/two_states_map.png)
+
+The spatial configuration shows no bias.
+But the aggregagate results may mask defficient protection for some taxa.
+Figure X shows the the density distribution of % habitat protected for each major taxa, under a market and BAU scenario with a 30% protection target.
+We find no evidence of bias in protection status between or within taxa groups.
+As with customary MPA implementation, more targeted policy interventions will be necessary for particularly vulnerable species (\emph{e.g.} harvest bans, export bans).
+
+<!-- ![Some figure should probably go here, showing the ggridges for each taxa group.](results/img/two_states_map.png) -->
+
+<!-- # Simulations -->
+
+<!-- The same approach can then be repeated for any level of spatial aggregation.
 As an example, I repeat the conservation excercise by subdividing the world into 12 Realms, and calculate realm-level supply curves to estimate the trading price for all countries that are part of that market.
+-->
 
-The following sections go into more detail to describe my methods.
+<!-- The following sections go into more detail to describe my methods.
 The first section describes the data, and important caveats are mentioned at this stage.
@@
 Finally, we discuss how the analysis can be replicated by creating markets at different spatial scales.
+-->
 
-## Spatial considerations
+<!-- ## Spatial considerations -->
 
-When combining different data sources, we also include pixel-level information about the Hemisphere, Realm, Province, and Ecoregion in which they reside.
+<!-- When combining different data sources, we also include pixel-level information about the Hemisphere, Realm, Province, and Ecoregion in which they reside.
 This allows us to repeat the exercise of finding supply curves for any level of spatial division in order to simulate markets within them.
 This is better described in the results section, where I present detailed methods and results in parallel.
+-->
 
-# Results
+<!-- # Results -->
 
-The main purpose of this project is to identify the gains from trade.
+<!-- The main purpose of this project is to identify the gains from trade.
 But in order to get there, there are other minor findings that are worth mentioning here.
@@
 Whenever relevant, I mention opportunities for improvements, and I later discuss them in the discussion section.
+-->
 
-## Global
+<!-- ## Global -->
 
-By combining costs and benefits of conservation and anticipating the ways in which countries may conserve within their waters, we can translate the (percent) area-based targets into biodiversity benefit targets.
+<!-- By combining costs and benefits of conservation and anticipating the ways in which countries may conserve within their waters, we can translate the (percent) area-based targets into biodiversity benefit targets.
 We find that a 30% target yields a global biodiversity benefit of 3 to 106, depending on the approach taken (Figure \ref{fig:eez-supply-curve-approaches}; Table \ref{tab:trading-prices}).
+-->
 
-![\label{fig:eez-supply-curve-approaches}Five sequential conservation approaches.
-Each line represents one nation.
-The y-axis shows how much conservation is achieved by protecting a given percentage (x-axis) of a nation's EEZ.
-The numbers show the totl biodiversity, summing across all nations.](results/img/eez_supply_curves_approaches.png)
+<!-- \newpage -->
+
+<!-- In translating the area-based target into a biodiversity benefit target we identified the global conservation benefits, but also the costs to each nation (Figure \ref{fig:equilibrium-supply-curves} left).
+We can use the nation-level supply curves and trading price to find the market's equilibrium for conservation (Figure \ref{fig:equilibrium-supply-curves} right).
+Under a market-based approach, in-situ conservation will decrease for some nations (those for which costs are higher than the trading price), while some may see increased in-situ conservation (those under the trading price).
+The additional conservation in some nations (red lines in Figure \ref{fig:equilibrium-supply-curves}) can only be achieved through a market, where nations whose in-situ conservation would exceed the trading price are willing to pay to conserve elsewhere.
+-->
+
+<!-- ![\label{fig:equilibrium-supply-curves} Supply curves for a case where nations efficiently conserve 30% in-situ (left) or with a market-based approach (right).
+The horizontal dashed line shows the trading price (131,241.92).
+Red lines in the right-side panel show the portion of additional conservation that is incentiviez by trade.](results/img/equilibrum_supply_curves.png) -->
+
+<!-- By knowing the equilibrium under each approach we can compare the total costs and calculate the gains from trade.
+We find that a market-based approach can produce the same biodiversity benefit of 71.56 units for just 54% of the costs (Table \ref{tab:gains-from-trade}).
+Of course, gains from trade are heterogeneously distributed among nations.
+The map below (Figure \ref{fig:map-of-trade}) shows which countries would rather pay to conserve elsewhere, and which countries get paid to conserve in-place.
+Figure \ref{fig:two-states-map} shows the outcome of each approach.
+-->
+
+<!-- \input{results/tab/gains_from_trade.tex} -->
 
@@
 
-Our global supply curve allows us to take any biodiversity target and find its corresponding costs.
-In doing so, we can identify the trading price for any possible target.
-We find that the trading price for conservation lies between 0.08 and 483,528^[I must stress that these figures represent losses in fisheries landings, not dollars, and that more work needs to be done.].
-Figure \ref{fig:global-conservation-targets-and-trading-prices} shows the corresponding trading prices for each of the targets outlined above.
-Table \ref{tab:trading-prices} shows the five targets and their trading prices.
-While these figures and table show only the values for the five approaches mentioned above, the same can be done for any given biodiversity target.
+<!-- ## Realms -->
 
-![\label{fig:global-conservation-targets-and-trading-prices} The global conservation supply curve, showing the costs for each of the biodiversity benefit targets.](results/img/global_conservation_targets_and_trading_prices.png)
-
-\input{results/tab/trading-prices.tex}
-
-\newpage
-
-In translating the area-based target into a biodiversity benefit target we identified the global conservation benefits, but also the costs to each nation (Figure \ref{fig:equilibrium-supply-curves} left).
-We can use the nation-level supply curves and trading price to find the market's equilibrium for conservation (Figure \ref{fig:equilibrium-supply-curves} right).
-Under a market-based approach, in-situ conservation will decrease for some nations (those for which costs are higher than the trading price), while some may see increased in-situ conservation (those under the trading price).
-The additional conservation in some nations (red lines in Figure \ref{fig:equilibrium-supply-curves}) can only be achieved through a market, where nations whose in-situ conservation would exceed the trading price are willing to pay to conserve elsewhere.
-
-![\label{fig:equilibrium-supply-curves} Supply curves for a case where nations efficiently conserve 30% in-situ (left) or with a market-based approach (right).
-The horizontal dashed line shows the trading price (131,241.92).
-Red lines in the right-side panel show the portion of additional conservation that is incentiviez by trade.](results/img/equilibrum_supply_curves.png)
-
-By knowing the equilibrium under each approach we can compare the total costs and calculate the gains from trade.
-We find that a market-based approach can produce the same biodiversity benefit of 71.56 units for just 54% of the costs (Table \ref{tab:gains-from-trade}).
-Of course, gains from trade are heterogeneously distributed among nations.
-The map below (Figure \ref{fig:map-of-trade}) shows which countries would rather pay to conserve elsewhere, and which countries get paid to conserve in-place.
-Figure \ref{ref:two-states-map} shows the outcome of each approach.
-
-\input{results/tab/gains_from_trade.tex}
-
-![\label{fig:map-of-trade}Map of trade.
-Blue indicates nations that reach the trading price before meeting their target, and therefore chose to pay to conserve elsewhere.
-Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/map_of_trade.png)
-
-![\label{ref:two-states-map} Map of two possible conservation outcomes.](results/img/two_states_map.png)
-
-\newpage
-
-## Realms
-
-The results presented so far assume that a unit of biodiversity is worth the same anywhere around the world.
+<!-- The results presented so far assume that a unit of biodiversity is worth the same anywhere around the world.
 However, we might want to ensure that no single type of habitat or region is left out.
@@
 \cite{spalding_2007} divided the oceans using a hierarchical approach with Realms (n = 12) containing Provinces (n = 60), which in turn contain Ecoregions (n = 219).
+-->
 
-The same approach as above can be repeated for any level of spatial aggregation that allows for more than one country.
+<!-- The same approach as above can be repeated for any level of spatial aggregation that allows for more than one country.
 For example, this can be done for each of the 12 realms (Figure \ref{fig:realm-map}).
@@
 For example, Mexico is present across four realms (Tropical Eastern Pacific, Temperate Northern Pacific, Temperate Northern Atlantic, and Tropical Atlantic).
+-->
 
-As done before for the global analysis, we can generate the biodiversity supply curves of each country-realm combination, and calculate the realm-level supply curve for biodiversity benefit.
+<!-- As done before for the global analysis, we can generate the biodiversity supply curves of each country-realm combination, and calculate the realm-level supply curve for biodiversity benefit.
 Then, for any desired level of biodiversity benefit, we can estimate the realm-specific trading price, and derive the market equilibrium.
 From there, we can estimate the gains from trade, and identify who gains from this approach.
+-->
 
-We first must find the target amount of biodiversity.
+<!-- We first must find the target amount of biodiversity.
 We do this by finding how much biodiversity would be protected if every country were to protect 30% of each realm present within their Exclusive Economic Zone ^[This is more closely aligned with what the IUCN 30% target is: the International Union for the Conservation of Nature (IUCN) has suggested that at least 30% of each marine habitat should be protected in areas with no extractive activities.].
@@
 Note how for the Temperate Northern Pacific Mexico gets paid to conserve, while in the Tropical Atlantic it pays to conserve elsewhere.
+-->
 
-So far, I have performed preliminary analyses for a global market and outlined how it would be done for 12 realms.
+<!-- So far, I have performed preliminary analyses for a global market and outlined how it would be done for 12 realms.
 I believe there is room (and need) to try a few more approaches.
@@
 In the end I will have six levels of spatial aggregation: global, hemisphere, ocean, realm, province, and EEZ (BAU).
+-->
+
+\newpage
+
+# Other figures and tables
 
@@
 ![\label{fig:realms-per-eezs} Number of realms in each Exclusive Economic Zone](results/img/realms_per_eez.png)
-
-![\label{fig:eez-rlm-supply-curve} Biodiversity supply curves for all nations within each realm (top panels), and realm-level biodiversity supply curves (bottom).
-For the small panels, each line represents a country.
-In the large bottom panel, each line represents the horizontally-summed supply curve for each realm (color coded).](results/img/eez_rlm_supply_curve.png)
-
-\input{results/tab/trading_prices_rlm.tex}
-
-\input{results/tab/gains_from_trade_rlm.tex}
-
-![\label{fig:rlm-map-of-trade}Map of trade for each realm.
-Blue indicates nations that reach the trading price before meeting their target, and therefore chose to pay to conerve elsewhere.
-Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/rlm_map_of_trade.png)
-
-\newpage
-
-# Other figures and tables
 
@@
 
+Bubbles
+
 ![\label{fig:realm-map}Map of the 12 realms, as defined by \cite{spalding_2007}.](results/img/realm_map.png)
 
-Map of provinces
+![\label{fig:realm-map}Map of the 60 provinces, as defined by \cite{spalding_2007}.](results/img/provinces_map.png)
 

### 2021-06-18 scripts/03_descriptive_content/02_plot_trading_units.R

@@ -77,8 +77,8 @@ lazy_ggsave(plot = rlm_per_eez,
 # Map marine ecoregions
 
 realm_map <- ggplot() +
-  geom_sf(data = coast) +
-  geom_sf(data = eez_meow, aes(fill = realm)) +
+  geom_sf(data = coast, color = "black", size = 0.1) +
+  geom_sf(data = eez_meow, aes(fill = realm), color = "black", size = 0.1) +
   ggtheme_map() +
   scale_fill_viridis_d() +
   labs(fill = "Realm") +
@@ -86,6 +86,22 @@ realm_map <- ggplot() +
 
 lazy_ggsave(plot = realm_map,
             filename = "realm_map",
+            width = 20, 
+            height = 10)
+
+
+# Provinces map
+
+provinces_map <- ggplot() +
+  geom_sf(data = coast, color = "black", size = 0.1) +
+  geom_sf(data = eez_meow, aes(fill = province), color = "black", size = 0.1) +
+  ggtheme_map() +
+  scale_fill_viridis_d() +
+  # labs(fill = "Realm") +
+  theme(legend.position = "None")
+
+lazy_ggsave(plot = provinces_map,
+            filename = "provinces_map",
             width = 20, 
             height = 10)
 

### 2021-07-16 scripts/02_processing/06_get_costs_and_benefits.R
Get css and benefits with hemisphere

@@ -62,11 +62,7 @@ pro_code <-
   raster(file.path(project_path, "processed_data", "pro_raster.tif")) %>% 
   crop(benefits_raster)
 
-eco_code <-
-  raster(file.path(project_path, "processed_data", "eco_raster.tif")) %>% 
-  crop(benefits_raster)
-
-seas_code <- raster(file.path(project_path, "processed_data", "world_seas_raster.tif")) %>% 
+hem_code <- raster(file.path(project_path, "processed_data", "hemispheres.tif")) %>% 
   crop(benefits_raster)
 
 # Load the EEZ vector data
@@ -74,19 +70,9 @@ eez_meow <-
   st_read(file.path(
     project_path,
     "processed_data",
-    "intersected_eez_and_meow.gpkg"
+    "intersected_eez_meow_hem.gpkg"
   )) %>% 
   st_drop_geometry() %>% 
-  as_tibble()
-
-# Load the world seas vectotr data
-world_seas <- st_read(file.path(
-  project_path,
-  "processed_data",
-  "clean_world_seas.gpkg"
-)) %>% 
-  st_drop_geometry() %>% 
-  rename(sea_name = name) %>% 
   as_tibble()
 
 ## PROCESSING ########################################################################
@@ -95,8 +81,7 @@ cb <-
   stack(iso3n,                   # Start by creating a raster stack of all features
         rlm_code,
         pro_code,
-        eco_code,
-        seas_code,
+        hem_code,
         benefits_raster,
         costs_raster) %>%
   as.data.frame(xy = T) %>%       # Convert to data.frame, but keep coordinates
@@ -106,61 +91,57 @@ cb <-
     iso3n = eez_raster,
     rlm_code = rlm_raster,
     pro_code = pro_raster,
-    eco_code = eco_raster,
-    sea_code = world_seas_raster,
-    benefit = suitability,
+    hem_code = hemispheres,
     cost = revenue_raster
   ) %>%
-  drop_na(iso3n, cost, benefit) %>%                             # Drop areas beyond national jurisdiction
-  mutate(hemisphere = case_when(lon > 0 & lat > 0 ~ "NE",
-                                lon < 0 & lat > 0 ~ "NW",
-                                lon > 0 & lat <= 0 ~ "SE",
[…]

### 2021-07-16 scripts/03_descriptive_content/01_plot_supply_curves.R
remove ecoregion plots

@@ -42,16 +42,6 @@ pro_h_sum <- readRDS(
   file = file.path( project_path, "processed_data", "pro_h_sum_costs_and_benefits.rds")
 )
 
-#E Ecoregion eez
-## For each ecoregion, province, realm, and EEZ
-eco_eez_cb <- readRDS(
-  file = file.path( project_path, "processed_data", "eco_eez_costs_and_benefits.rds")
-)
-### Horizonbtaly summed for each ecoregion
-eco_eez_cb <- readRDS(
-  file = file.path( project_path, "processed_data", "eco_h_sum_costs_and_benefits.rds")
-)
-
 # PROCESSING ############################################################################################
 
 # Global curve

### 2021-07-16 scripts/03_descriptive_content/02_plot_trading_units.R
remove ecoregions

@@ -13,9 +13,8 @@ eez_h_sum_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_h_
 eez_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_costs_and_benefits.rds"))
 rlm_eez_cb <- readRDS(file = file.path(project_path, "processed_data", "rlm_eez_costs_and_benefits.rds"))
 pro_eez_cb <- readRDS(file = file.path(project_path, "processed_data", "pro_eez_costs_and_benefits.rds"))
-eco_eez_cb <- readRDS(file = file.path(project_path, "processed_data", "eco_eez_costs_and_benefits.rds"))
 
-eez_meow <- st_read(file.path(project_path, "processed_data", "intersected_eez_and_meow.gpkg")) %>% 
+eez_meow <- st_read(file.path(project_path, "processed_data", "intersected_eez_meow_hem.gpkg")) %>% 
   ms_simplify()
 
 # Load a coastline
@@ -26,10 +25,9 @@ coast <- ne_countries(returnclass = "sf") %>%
 meows_per_eez <- eez_meow %>% 
   group_by(iso3) %>% 
   summarize(n_rlm = n_distinct(realm),
-            n_pro = n_distinct(province),
-            n_eco = n_distinct(ecoregion)) %>% 
+            n_pro = n_distinct(province)) %>% 
   ungroup() %>% 
-  arrange(desc(n_eco)) %>% 
+  arrange(desc(n_pro)) %>% 
   ms_simplify(keep_shapes = TRUE)
 
 rlm_per_eez <- ggplot() +
@@ -50,18 +48,8 @@ pro_per_eez <- ggplot() +
   guides(fill = guide_colorbar(frame.colour = "black",
                                ticks.colour = "black"))
 
-eco_per_eez <- ggplot() +
-  geom_sf(data = meows_per_eez, aes(fill = n_eco)) +
-  geom_sf(data = coast) +
-  scale_fill_viridis_c() +
-  ggtheme_map() +
-  labs(fill = "# of\nEcoregions") +
-  guides(fill = guide_colorbar(frame.colour = "black",
-                               ticks.colour = "black"))
-
 meows_per_eez_plot <- plot_grid(rlm_per_eez,
                            pro_per_eez,
-                           eco_per_eez,
                            ncol = 1,
                            labels = "AUTO")
 
[…]

### 2021-07-16 scripts/03_descriptive_content/04_mex_us_example_benefits_costs_bcr.R
Added example of Mexico and the US

@@ -1,0 +1,106 @@
+####################################################
+# Now that we have the targets and prices, we can 
+# move forward and identify where biodiversity is
+# protected, and the associated costs of doing so.
+# 
+# The benefits should be equivalent, since we are
+# using the same target.
+####################################################
+
+# SET UP ################################################################################################
+# Load packages
+library(startR)
+library(raster)
+library(rnaturalearth)
+library(cowplot)
+library(sf)
+library(tidyverse)
+
+# Load data
+
+## master data
+master_cb <- readRDS(file = file.path(project_path, "processed_data", "master_costs_and_benefits.rds")) %>% 
+  filter(iso3 %in% c("MEX", "USA")) %>% 
+  filter(!realm %in% c("Arctic", "Eastern Indo-Pacific"))
+
+eez_cb <- readRDS(
+  file = file.path(project_path, "processed_data", "eez_costs_and_benefits.rds")) %>% 
+  filter(iso3 %in% c("MEX", "USA")) %>% 
+  filter(!realm %in% c("Arctic", "Eastern Indo-Pacific"))
+
+coastline <- ne_countries(returnclass = "sf",scale = "large") %>% 
+  filter(iso_a3 %in% c("MEX", "USA")) %>% 
+  st_transform(epsg_moll)
+
+## PLOT IT
+
+# Benefits
+
+benefit_map <- ggplot() +
+  geom_tile(data = master_cb, aes(x = lon, y = lat, fill = benefit / 2500)) +
+  geom_sf(data = coastline, color = "black", size = 0.5) +
+  # coord_sf(crs = proj_longlat) +
+  ggtheme_map() +
+  labs(fill = bquote("Habitat\nsuitability")) +
+  scale_fill_viridis_c() +
+  guides(fill = guide_colorbar(frame.colour = "black",
+                               ticks.colour = "black")) +
+  # theme(legend.position = "bottom") +
+  lims(y = c(1500000, 5900000),
+       x = c(-11900000, -5500000)) +
+  ggtitle(label = "Habitat suitability is heterogeneously\ndistributed between and within nations",
+          subtitle = "All pixels are 50 X 50 km")
+
+
+
+cost_map <- ggplot() +
+  geom_tile(data = master_cb, aes(x = lon, y = lat, fill = cost / 1e6)) +
+  geom_sf(data = coastline, color = "black", size = 0.5) +
[…]

### 2021-07-16 scripts/04_analysis/01_get_targets.R
Removed redundant scripts to get targets and prices

@@ -1,197 +1,0 @@
-#######################################################
-# There are many ways the 30% can be interpreted. Each
-# country may decide to protect their 30% in a
-# different way. For example, by protecting the 30% with
-# the highest biodiversity, or the 30% with the least cost.
-# 
-# To avoid abcriguities, I calculate the country-level
-# biodiversity benefit of conserving 30% with the
-# the folloeing rules:
-# 
-# - Most efficient (benefit / cost)
-# - Most conservtion (benefit)
-# - Least cosnervation (-benefit)
-# - Most costly (cost)
-# - Cheapest (-cost)
-# 
-# I then calculate the global biodiversity benefit by
-# summing across all nations. These 5 nubcrers represent
-# plausible global biodiversity targets.
-#######################################################
-
-
-
-# SET UP ################################################################################################
-# Load packages
-library(startR)
-library(tidyverse)
-
-# Load data
-eez_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_costs_and_benefits.rds")) %>% 
-  mutate(type = "efficient") %>% 
-  select(iso3, everything())
-
-eez_h_sum_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_h_sum_costs_and_benefits.rds")) %>% 
-  mutate(type = "efficient") %>% 
-  select(iso3, everything())
-
-# PROCESSING #############################################################################################
-# The processing part sorts the dataset (ascending and descending) by the relevant variable (cost or benefit)
-# It then calculates the total benefit (using the "get_country_pathways" function),
-# as well as the percentage contribution. The process is done globally and for each country.
-
-## Global
-# Most efficient
-agg_cb <- eez_cb %>% 
-  arrange(desc(bcr)) %>% 
-  get_country_pathways() %>% 
-  mutate(type = "efficient")
-
-# Maximize conservation
-max_con_agg <- eez_cb %>% 
-  arrange(desc(benefit)) %>% 
-  get_country_pathways() %>% 
-  mutate(type = "maximize conservation")
-
-# Minimize conservation
[…]

### 2021-07-16 scripts/04_analysis/03_get_eez_level_conservation.R
Updated analysis for EEZ level 30%

@@ -27,9 +27,10 @@ eez_cb <- readRDS(
 )
 
 ## Read trading prices
-trading_prices <- readRDS(
-  file = file.path(project_path, "output_data", "global_trading_prices.rds")
-)
+trading_price <- eez_h_sum_cb %>% 
+  filter(pct_area <= 0.3) %>% 
+  pull(mc) %>% 
+  max()
 
 # Load a coastline
 coast <- ne_countries(returnclass = "sf") %>% 
@@ -56,16 +57,16 @@ conserving_nations <- eez_cb %>%
 
 ## Identify conserved patches
 # Get the most efficient trading price
-trading_price <- trading_prices %>% 
-  filter(type == "efficient") %>% 
-  pull(mc)
+# trading_price <- trading_prices %>% 
+  # filter(type == "efficient") %>% 
+  # pull(mc)
 
 # Filter to keep only the protected places
 bau <- eez_cb %>% 
   group_by(iso3) %>% 
-  mutate(min_pct = min(pct, na.rm = T)) %>% 
+  mutate(min_pct = min(pct_area, na.rm = T)) %>% 
   ungroup() %>% 
-  filter(pct <= 0.3 | pct <= min_pct) %>%      # Keep the most efficient 30% of each country OR the first patch
+  filter(pct_area <= 0.3 | pct_area <= min_pct) %>%      # Keep the most efficient 30% of each country OR the first patch
   mutate(approach = "bau")
   
 mkt <- eez_cb %>% 
@@ -154,23 +155,6 @@ benefit_supply_curves <- bau %>%
        caption = "NOTE: Axis have been cropped for visualization purposes") +
   guides(color = FALSE)
 
-market_gains_plot <- combined_outcomes %>% 
-  select_if(is.numeric) %>% 
-  select(-contains("stop")) %>% 
-  summarize_all(sum, na.rm = T) %>% 
-  gather(variable, value) %>% 
-  separate(variable, into = c("approach", "variable")) %>% 
-  mutate(variable = case_when(variable == "tc" ~ "Total costs",
-                              variable == "tb" ~ "Quality-weighed area",
-                              variable == "area" ~ "Area")) %>% 
-  ggplot(aes(x = approach, y = value, fill = approach)) +
-  geom_col(position = "dodge", color = "black") +
-  facet_wrap(~variable, scale = "free_y", ncol = 1) +
-  scale_fill_brewer(palette = "Set1", guide = F) +
-  ggtheme_plot() +
-  labs(x = "Approach", y = "Value") +
[…]

### 2021-07-16 scripts/04_analysis/05_realm_level_market.R
Updaed 30% cons for realm

@@ -34,7 +34,7 @@ coast <- ne_countries(returnclass = "sf") %>%
 eez <- st_read(
   file.path(project_path,
             "processed_data",
-            "intersected_eez_and_meow.gpkg")
+            "intersected_eez_meow_hem.gpkg")
 ) %>% 
   mutate(has_obligations = iso3 %in% unique(rlm_eez_cb$iso3)) %>%
   rmapshaper::ms_simplify(keep_shapes = T, sys = T) %>%
@@ -47,19 +47,13 @@ conserving_nations <- rlm_eez_cb %>%
 
 # PROCESSING ############################################################################################
 
-# Get targets
-rlm_conservation_target <- rlm_eez_cb %>%
-  group_by(realm) %>%
-  nest() %>%
-  mutate(target = map_dbl(data, benefit, 0.3)) %>%
-  select(-data)
 
 rlm_trading_prices <- rlm_h_sum %>% 
   group_by(realm) %>% 
-  nest() %>% 
-  left_join(rlm_conservation_target, by = "realm") %>% 
-  mutate(trading_price = map2_dbl(.x = target, .y = data, get_trading_price)) %>% 
-  select(-data)
+  filter(pct_area <= 0.3) %>% 
+  slice_max(mc) %>% 
+  ungroup() %>% 
+  select(realm, trading_price = mc)
 
 ## Identify conserved patches
 # Get the most efficient trading price
@@ -110,7 +104,7 @@ combined_outcomes <- conserving_nations %>%
 # Find stopping prices
 stops <- combined_outcomes %>% 
   filter(bau_tb <= mkt_tb) %>% 
-  select(iso3, mc_stop) %>% 
+  select(iso3, realm, mc_stop) %>% 
   mutate(approach = "mkt")
 
 gains_from_trade <- combined_outcomes %>% 
@@ -140,7 +134,9 @@ eez_with_results <- eez %>%
 
 ## FIGURES #########################################################################
 ## Plot the supply curves where they stop
-benefit_supply_curves <- rbind(bau, mkt %>% select(-target)) %>%
+benefit_supply_curves <- bau %>% 
+  select(-min_pct) %>% 
+  rbind(mkt %>% select(-trading_price)) %>%
   left_join(stops, by = c("iso3", "realm", "approach"), fill = list(mc_stop = 0)) %>% 
   mutate(mkt_gain = mc >= mc_stop,
[…]

### 2021-07-16 scripts/04_analysis/06_province_level_market.R
Updated anakysis for 30% cons at province

@@ -33,35 +33,42 @@ pro_h_sum <- readRDS(
 coast <- ne_countries(returnclass = "sf") %>% 
   st_transform(crs = epsg_moll) 
 
+# Load EEZ geopackage
+eez <- st_read(
+  file.path(project_path,
+            "processed_data",
+            "intersected_eez_meow_hem.gpkg")
+) %>% 
+  mutate(has_obligations = iso3 %in% unique(pro_eez_cb$iso3)) %>%
+  rmapshaper::ms_simplify(keep_shapes = T, sys = T) %>%
+  st_make_valid() %>%
+  filter(iso3 %in% unique(pro_eez_cb$iso3))
+
+conserving_nations <- pro_eez_cb %>% 
+  select(iso3, province) %>% 
+  distinct()
+
 # PROCESSING ############################################################################################
 
-# Get targets
-pro_conservation_target <- pro_eez_cb %>%
-  group_by(province) %>%
-  nest() %>%
-  mutate(target = map_dbl(data, benefit, 0.3)) %>%
-  select(-data)
 
 pro_trading_prices <- pro_h_sum %>% 
   group_by(province) %>% 
-  nest() %>% 
-  left_join(pro_conservation_target, by = "province") %>% 
-  mutate(trading_price = map2_dbl(.x = target, .y = data, get_trading_price)) %>% 
-  select(-data)
-
+  filter(pct_area <= 0.3) %>% 
+  slice_max(mc) %>% 
+  ungroup() %>% 
+  select(province, trading_price = mc)
 ## Identify conserved patches
 # Get the most efficient trading price
 
 # Filter to keep only the protected places
 bau <- pro_eez_cb %>% 
-  filter(pct <= 0.3) %>%                       # Keep the most efficient 30% of each country - province
+  filter(pct_area <= 0.3) %>%                       # Keep the most efficient 30% of each country - province
   mutate(approach = "bau")
 
 mkt <- pro_eez_cb %>% 
   left_join(pro_trading_prices, by = c("province")) %>%
   filter(mc <= trading_price) %>%              # Keep all patches in each country with a cost < trading price
-  mutate(approach = "mkt") %>% 
-  select(-c(trading_price,))
+  mutate(approach = "mkt")
 
 ## Calculate country-level summaries
 # For BAU
@@ -75,11 +82,23 @@ realized_bau_cb <- bau %>%
 
 # For a market
 realized_mkt_cb <- mkt %>% 
-  group_by(approach, iso3, province) %>% 
[…]

### 2021-07-16 scripts/04_analysis/08_all_segments_all_scenarios.R
Running all segments and all scenarios

@@ -40,13 +40,6 @@ pro_h_sum <- readRDS(
   file = file.path( project_path, "processed_data", "pro_h_sum_costs_and_benefits.rds")
 )
 
-sea_eez_cb <- readRDS(
-  file = file.path( project_path, "processed_data", "sea_eez_costs_and_benefits.rds")
-  )
-sea_h_sum <- readRDS(
-  file = file.path( project_path, "processed_data", "sea_h_sum_costs_and_benefits.rds")
-  )
-
 
 get_global_market_gains <- function(eez_cb, r, trading_price) {
   
@@ -58,9 +51,9 @@ get_global_market_gains <- function(eez_cb, r, trading_price) {
   
   bau <- eez_cb %>% 
     group_by(iso3) %>% 
-    mutate(min_pct = min(pct, na.rm = T)) %>% 
+    mutate(min_pct = min(pct_area, na.rm = T)) %>% 
     ungroup() %>% 
-    filter(pct <= r | pct <= min_pct) %>% # Keep the most efficient r% of each country - hemisphere
+    filter(pct_area <= r | pct_area <= min_pct) %>% # Keep the most efficient r% of each country - hemisphere
     mutate(approach = "bau") %>% 
     group_by(approach, iso3) %>% 
     summarize(bau_tb = sum(benefit, na.rm = T),
@@ -116,9 +109,9 @@ get_segmented_market_gains <- function(curves, r, trading_prices, group) {
   # Filter to keep only the protected places
   bau <- curves %>% 
     group_by_at(c("iso3", group)) %>% 
-    mutate(min_pct = min(pct, na.rm = T)) %>% 
+    mutate(min_pct = min(pct_area, na.rm = T)) %>% 
     ungroup() %>% 
-    filter(pct <= r | pct <= min_pct) %>%                       # Keep the most efficient 30% of each country - hemisphere
+    filter(pct_area <= r | pct_area <= min_pct) %>%                       # Keep the most efficient 30% of each country - hemisphere
     mutate(approach = "bau")
   
   mkt <- curves %>% 
@@ -238,20 +231,11 @@ gains_from_trade_multiple_scenarios_pro <-
     group = "province"
   )
 
-gains_from_trade_multiple_scenarios_sea <- 
-  market_segmenter(
-    rs = rs,
-    curves = sea_eez_cb,
-    agg_curves = sea_h_sum,
-    group = "sea_name"
-  )
-
[…]

### 2021-11-09 scripts/03_descriptive_content/01_plot_supply_curves.R
Updating all

@@ -46,19 +46,19 @@ pro_h_sum <- readRDS(
 
 # Global curve
 global <- ggplot(data = eez_h_sum,
-                 mapping = aes(x = tb, y = mc)) +
+                 mapping = aes(x = tb / 1e3, y = mc)) +
   geom_line(size = 1) +
   ggtheme_plot() +
-  labs(x = bquote("Surface area (HS weighted;"~Km^2~")"),
+  labs(x = bquote("Surface area (HS weighted; thousand"~Km^2~")"),
        y = bquote("Fisheries revenue ($"~Km^-2~")"))
 
 # Country-level supply curves
 eez <- ggplot(data = eez_cb,
-              mapping = aes(x = tb, y = mc, group = iso3)) +
+              mapping = aes(x = tb / 1e3, y = mc, group = iso3)) +
   geom_line() +
   guides(color = F) +
   ggtheme_plot() +
-  labs(x = bquote("Surface area (HS weighted;"~Km^2~")"),
+  labs(x = bquote("Surface area (HS weighted; Thousand "~Km^2~")"),
        y = bquote("Fisheries revenue ($"~Km^-2~")"))
 
 eez_supply_curve <- plot_grid(eez, global, ncol = 2, labels = "AUTO")
@@ -72,7 +72,7 @@ eez_rlm <-
   scale_color_viridis_d() +
   facet_wrap( ~ realm, scales = "free") +
   ggtheme_plot() +
-  labs(x = bquote("Surface area (HS weighted;"~Km^2~")"),
+  labs(x = bquote("Surface area (HS weighted; Thousand"~Km^2~")"),
        y = bquote("Fisheries revenue ($"~Km^-2~")"))
 
 # realm summed
@@ -102,7 +102,7 @@ eez_pro <-
 # EXPORT PLOTS ##############################################################################################
 lazy_ggsave(plot = eez_supply_curve,
             filename = "eez_supply_curve",
-            width = 12, height = 5)
+            width = 18, height = 7)
 
 lazy_ggsave(plot = eez_rlm_supply_curve ,
             filename = "eez_rlm_supply_curve",

### 2021-11-09 scripts/03_descriptive_content/02_plot_trading_units.R

@@ -73,6 +73,20 @@ lazy_ggsave(plot = realm_map,
             width = 20, 
             height = 10)
 
+# Hemisphere map
+
+hemisphere_map <- ggplot() +
+  geom_sf(data = coast, color = "black", size = 0.1) +
+  geom_sf(data = eez_meow, aes(fill = hemisphere), color = "black", size = 0.1) +
+  ggtheme_map() +
+  scale_fill_viridis_d() +
+  labs(fill = "Hemisphere") +
+  theme(legend.position = "bottom")
+
+lazy_ggsave(plot = hemisphere_map,
+            filename = "hemisphere_map",
+            width = 20, 
+            height = 10)
 
 # Provinces map
 

### 2021-11-09 scripts/04_analysis/03_get_eez_level_conservation.R

@@ -56,10 +56,6 @@ conserving_nations <- eez_cb %>%
   distinct()
 
 ## Identify conserved patches
-# Get the most efficient trading price
-# trading_price <- trading_prices %>% 
-  # filter(type == "efficient") %>% 
-  # pull(mc)
 
 # Filter to keep only the protected places
 bau <- eez_cb %>% 
@@ -100,9 +96,13 @@ combined_outcomes <- conserving_nations %>%
     mkt_tb = 0, mkt_tc = 0, mkt_area = 0,
     bau_tb = 0, bau_tc = 0, bau_area = 0)) %>% 
   select(-contains("app")) %>% 
-  mutate(transaction = ifelse(mkt_tc < bau_tc, "Pays", "Gets paid"),
-         mkt_tc_else = mkt_tc - bau_tc) %>% 
-  select(iso3, contains("bau"), contains("mkt"), transaction)
+  mutate(transaction = ifelse(mkt_tc < bau_tc, "Buyers", "Sellers"),
+         rect = abs(bau_tb - mkt_tb) * trading_price,
+         mkt_tc_b = bau_tc - mkt_tc - rect,
+         mkt_tc_s = rect - mkt_tc + bau_tc,
+         savings = ifelse(mkt_tb < bau_tb, mkt_tc_b, mkt_tc_s),
+         ratio = savings / bau_tc) %>% 
+  select(iso3, contains("bau"), contains("mkt"), savings, transaction, rect, ratio, everything())
 
 # Find stopping prices
 stops <- combined_outcomes %>% 
@@ -111,25 +111,25 @@ stops <- combined_outcomes %>%
   mutate(approach = "mkt")
 
 
-gains_from_trade <- combined_outcomes %>% 
-  select_if(is.numeric) %>% 
-  select(-contains("stop")) %>% 
-  summarize_all(sum, na.rm = T) %>% 
-  gather(variable, value) %>% 
-  separate(variable, into = c("approach", "variable")) %>% 
-  spread(approach, value) %>% 
-  mutate(difference = bau - mkt,
-         ratio = mkt / bau)
+# gains_from_trade <- combined_outcomes %>% 
+#   select_if(is.numeric) %>% 
+#   select(-contains("stop")) %>% 
+#   summarize_all(sum, na.rm = T) %>% 
+#   gather(variable, value) %>% 
+#   separate(variable, into = c("approach", "variable")) %>% 
+#   spread(approach, value) %>% 
[…]

### 2021-11-09 scripts/04_analysis/08_all_segments_all_scenarios.R

@@ -204,7 +204,11 @@ gains_from_trade_multiple_scenarios <- rbind(
   gains_from_trade_multiple_scenarios_rlm,
   gains_from_trade_multiple_scenarios_pro) %>% 
   mutate(bubble = stringr::str_to_sentence(bubble),
-         bubble = fct_relevel(bubble, "Province", after = Inf))
+         bubble = case_when(bubble == "Global" ~ "Global (N = 1)",
+                            bubble == "Hemisphere" ~ "Hemisphere (N = 4)",
+                            bubble == "Realm" ~ "Realm (N = 12)",
+                            bubble == "Province" ~ "Province (N = 60)"),
+         bubble = fct_relevel(bubble, "Province (N = 60)", after = Inf))
 
 # Visualize 
 abs <- ggplot(gains_from_trade_multiple_scenarios, aes(x = r, y = difference, color = bubble)) +

### 2021-11-09 scripts/01_cleaning/01_clean_EEZs.R
Mving to a long-lat analysis

@@ -40,17 +40,11 @@ eez <- st_read(dsn = file.path(data_path,
                         iso_sov1,
                         iso_ter1)) %>% 
   select(iso3) %>%                                    # Select relevant columns
-  st_wrap_dateline() %>% 
-  st_make_valid() %>%                                 # Make all polygons valid
   group_by(iso3) %>%                                  # Union geometries
   summarize(a = 1) %>%
   ungroup() %>%
   select(-a) %>% 
   st_make_valid() %>%
-  ms_simplify(keep_shapes = T) %>%
-  st_make_valid() %>% 
-  st_transform(crs = proj_moll) %>%                   # Reproject to moll
-  st_make_valid() %>% 
   mutate(iso3n = countrycode(iso3, "iso3c", "iso3n")) %>% 
   select(iso3, iso3n)
 

### 2021-11-09 scripts/01_cleaning/02_clean_MEOWs.R

@@ -44,13 +44,12 @@ meow <- st_read(dsn = file.path(project_path,
                                 "raw_data", "MEOW"),
                 layer = "meow_ecos") %>% 
   clean_names() %>%                             # Clean column names
-  st_crop(xmin = -180L, xmax = 180L,
-          ymin = -90L, ymax = 90L) %>% 
-  st_transform(proj_moll) %>%                # Reproject to Moll
-  st_make_valid() %>%                           # Make sure all elements are valid
-  select(ecoregion, eco_code,                   # Select relevant colmns
-         province, pro_code = prov_code,
-         realm, rlm_code)
+  select(province, pro_code = prov_code,
+         realm, rlm_code) %>% 
+  group_by(province, pro_code,
+           realm, rlm_code) %>% 
+  summarize(a = 1) %>% 
+  ungroup()
 
 ## Export ###########################################################################
 meow_fn <- file.path(project_path, "processed_data", "clean_meow.gpkg")      # Define filename

### 2021-11-09 scripts/01_cleaning/03_clean_world_seas.R

@@ -34,9 +34,7 @@ library(tidyverse)
 world_seas <- st_read(dsn = file.path(data_path,
                                 "world-seas-v3", "World_Seas_IHO_v3"),
                 layer = "World_Seas_IHO_v3") %>% 
-  clean_names() %>%                             # Clean column names
-  st_transform(proj_moll) %>%                  # Reproject to Moll
-  st_make_valid() %>%                          # Make sure all elements are valid
+  clean_names() %>%                            # Clean column names
   select(name, mrgid) %>%                      # Select relevant columns
   st_collection_extract()                      # Make sure we don't have geometry collections
 

### 2021-11-09 scripts/01_cleaning/04_create_base_raster.R

@@ -1,19 +1,30 @@
+######################################################
+#title#
+######################################################
+# 
+# Purpose
+#
+######################################################
+
+
 # create base raster
 library(raster)
 library(tidyverse)
 
 # Create a raster object with the World's extent
-base_raster <- raster(xmn = -180, xmx = 180,
-                      ymn = -90, ymx = 90,
-                      resolution = 0.1,                # Set resolution to 0.1 of a degree (~10 km at the equator)
-                      vals = 1L,                       # Assign everything a value of 1L
-                      crs = proj_longlat) %>%          # Specify LongLat projection
-  projectRaster(res = 50000,                           # Specify desired end resolution (50 km grid-cells)
-                crs = proj_moll,                       # Specify Mollweide projection
-                method = "ngb",                        # Use NGB to ensure that they are all 1L in the end
-                over = T)                              # Allow to wrap around dateline
-                
+base_raster <- raster(
+  xmn = -180,
+  xmx = 180,
+  ymn = -90,
+  ymx = 90,
+  resolution = 0.5,                                                             # Set resolution to 0.1 of a degree (~10 km at the equator)
+  vals = 1L,                                                                    # Assign everything a value of 1L
+  crs = proj_longlat                                                            # Specify LongLat projection
+)
+
 # Export the base raster
-writeRaster(base_raster,
-            filename = file.path(project_path, "processed_data", "base_raster.tif"),
-            overwrite = TRUE)
+writeRaster(
+  base_raster,
+  filename = file.path(project_path, "processed_data", "base_raster.tif"),
+  overwrite = TRUE
+)

### 2021-11-09 scripts/01_cleaning/05_create_ocean_mask.R

@@ -1,18 +1,27 @@
+######################################################
+#title#
+######################################################
+#
+# Purpose
+#
+######################################################
 
 library(raster)
 library(fasterize)
-library(rnaturalearth)
 library(sf)
 library(tidyverse)
 
 
-world_seas <- st_read(file.path(project_path, "processed_data", "clean_world_seas.gpkg"))
+world_seas <-
+  st_read(file.path(project_path, "processed_data", "clean_world_seas.gpkg"))   # Read world seas
 
-base_raster <- raster(file.path(project_path, "processed_data", "base_raster.tif"))
+base_raster <-
+  raster(file.path(project_path, "processed_data", "base_raster.tif"))          # Read the base raster
 
-ocean_mask <- fasterize(world_seas, raster = base_raster)
-plot(ocean_mask)
+ocean_mask <- fasterize(world_seas, raster = base_raster)                       # Generate an ocean mask
 
-writeRaster(ocean_mask,
-            filename = file.path(project_path, "processed_data", "ocean_mask.tif"),
-            overwrite = TRUE)
+writeRaster(
+  ocean_mask,
+  filename = file.path(project_path, "processed_data", "ocean_mask.tif"),
+  overwrite = TRUE
+)

### 2021-11-09 scripts/02_processing/01_generate_pixel_benefits.R

@@ -1,88 +1,79 @@
+######################################################
+#title#
+######################################################
+# 
+# Purpose
+#
+######################################################
 
-## Load packages
+## SET UP ######################################################################
+# Load packages
 library(raster)
+library(data.table)
+library(janitor)
 library(sf)
 library(tidyverse)
 
-# Load ocean mask to remove rogue pixels
-ocean_mask <- raster(
-  file.path(project_path, "processed_data", "ocean_mask.tif")
+# Load data
+
+# Read in AquaMaps list of species (this is the list for which AM has available data)
+# Tidy it up to match the same format as our list of species of interest
+aquamaps_list <-
+  read_csv(
+    file.path(data_path, "aquamaps-v10-2019", "speciesoccursum.csv"),
+    col_types = cols(
+      SpeciesID = col_character(),
+      SpecCode = col_double(),
+      Genus = col_character(),
+      Species = col_character(),
+      FBname = col_character(),
+      OccurCells = col_double(),
+      Kingdom = col_character(),
+      Phylum = col_character(),
+      Class = col_character(),
+      Order = col_character(),
+      Family = col_character()
+    )
+  ) %>%
+  clean_names() %>%
+  filter(occur_cells >= 10) %>%
+  mutate(sci_name = paste(genus, species)) %>%
+  select(family, genus, sci_name, species_id)
+
+## PROCESSING ##################################################################
+# Create a vector of unique species
+spec_codes <- aquamaps_list %>%
+  pull(species_id) %>%
+  unique()
+
+# length(spec_codes) # Number of species contained in our analysis
+
+# Load all aquamaps data
+suitability_df <-
+  fread(
+    file = file.path(
+      data_path, "aquamaps-v10-2019", "hcaf_species_native.csv"
+      )
+    ) %>%
+  clean_names() %>%                                                             # Clean column names
+  .[species_id %in% spec_codes] %>%                                             # Keep only species with 10 or more records
+  .[probability >= 0.5] %>%                                                     # Keep only probability of existing
+  as_tibble() %>%                                                               # Convert to a tibble
+  group_by(center_long, center_lat) %>%                                         # Group by pixel
+  summarize(probability = mean(probability, na.rm = T))                         # Calculate the mean probability of each pixel
+
+
+# Rasterize suitability
+suitability <-
+  rasterFromXYZ(
[…]

### 2021-11-09 scripts/02_processing/03_generate_pixel_costs.R

@@ -1,5 +1,6 @@
 
 
+
 ## Set up
 
 # Load packages
@@ -8,81 +9,77 @@ library(data.table)
 library(tidyverse)
 
 # Load ocean mask to remove rogue pixels
-ocean_mask <- raster(
-  file.path(project_path, "processed_data", "ocean_mask.tif")
-)
+ocean_mask <- raster(file.path(project_path, "processed_data", "ocean_mask.tif"))
 
 # Read in catch data
 # List all catch files for industrial fisheries
-ind <- list.files(path = file.path(rw_path, "industrial"),
-                          pattern = "*.csv",
-                          full.names = T)
+ind <- list.files(
+  path = file.path(rw_path, "industrial"),
+  pattern = "*.csv",
+  full.names = T
+)
 
 # List all non-industrial fisheries
-Nind <- list.files(path = file.path(rw_path, "nonindustrial"),
-                    pattern = "*.csv",
-                    full.names = T)
+Nind <- list.files(
+  path = file.path(rw_path, "nonindustrial"),
+  pattern = "*.csv",
+  full.names = T
+)
 
 
-catch_files <- c(ind, Nind)                                                                  # Combine all file paths
-catch_files <- catch_files[str_detect(catch_files, "2005|2010|2015")]                        # Keep only file names for 2005-2015
+catch_files <- c(ind, Nind)                                                     # Combine all file paths
+
+catch_files <-
+  catch_files[str_detect(catch_files, "2005|2010|2015")]                        # Keep only file names for 2005-2015
 
 # Read all
-dt <- map_dfr(catch_files, fread, sep = ",", key = c("Cell", "ID")) %>%                      # Mad across files to read them in
+dt <-
+  map_dfr(catch_files,
+          fread,
+          sep = ",",
+          key = c("Cell", "ID")) %>%                                            # Map across files to read them in
   .[, .(ID, Cell, Reported)]
 
 # Read in the codes
-cell_codes <- readxl::read_excel(file.path(rw_path, "Codes.xlsx"), sheet = 1L) %>%           # Read in the codes
-  as.data.table(key = "Cell")                                                                # Convert to data.table; set key to Cell
+cell_codes <-
+  readxl::read_excel(file.path(rw_path, "Codes.xlsx"), sheet = 1L) %>%          # Read in the codes
+  as.data.table(key = "Cell")                                                   # Convert to data.table; set key to Cell
 
-taxa_codes <- readRDS(
[…]

### 2021-11-09 scripts/02_processing/04_intersect_eez_and_meow.R

@@ -17,29 +17,17 @@ library(tidyverse)
 
 
 # Load shapefiles
-eez <- st_read(file.path(project_path, "data", "clean_world_eez_v11.gpkg"))      # Load clean EEZ
-meow <- st_read(dsn = file.path(project_path, "data", "clean_meow.gpkg"))        # Load clean MEOW
+eez <- st_read(file.path(project_path, "processed_data", "clean_world_eez_v11.gpkg"))      # Load clean EEZ
+meow <- st_read(dsn = file.path(project_path, "processed_data", "clean_meow.gpkg"))        # Load clean MEOW
 
 ## Process #########################################################################################################
 # Intersect two shapefiles and generate some summary statistics ----------------------------------------------------
-eez_meow <- st_intersection(eez, meow) %>%                    # Intersect features
-  mutate(area_eco = st_area(.)) %>%                           # Calculate the area of each ecorgion within a country
-  group_by(iso3, iso3n, province, pro_code) %>%                                # Calculate area of each province within a country
-  mutate(area_pro = sum(area_eco, na.rm = T)) %>% 
-  ungroup() %>% 
-  group_by(iso3, iso3n, realm, rlm_code) %>%                                   # Calculate area of each realm within a country
-  mutate(area_rea = sum(area_eco, na.rm = T)) %>% 
-  ungroup() %>% 
-  group_by(iso3, iso3n) %>%                                          # Calculate EEZ area
-  mutate(area_eez = sum(area_eco, na.rm = T)) %>% 
-  ungroup() %>% 
-  mutate(eco_div_eez = area_eco / area_eez,                   # Calculate ratio of polygon area to EEZ area
-         pro_div_eez = area_pro / area_eez,
-         rea_div_eez = area_rea / area_eez) %>% 
-  select(iso3, iso3n, area_eez,                                      # Keep only rlevant columns
-         ecoregion, eco_code, area_eco, eco_div_eez,
-         province, pro_code, area_pro, pro_div_eez,
-         realm, rlm_code, area_rea, rea_div_eez)
+eez_meow <- eez %>% 
+  # st_crop(xmin = -180, ymin = -90, xmax = 180, ymax = 90) %>%
+  st_intersection(meow) %>% 
+  select(iso3, iso3n,                                                 # Keep only relevant columns
+         province, pro_code,
+         realm, rlm_code)
 
 ## Export -----------------------------------------------------------------------------------------------------------
[…]

### 2021-11-09 scripts/02_processing/05_rasterize_eez_meow_seas.R

@@ -26,8 +26,6 @@ world_seas <- st_read(file.path(project_path, "processed_data", "clean_world_sea
 eez_raster <- fasterize(eez_meow, base_raster, field = "iso3n")
 realm_raster <- fasterize(eez_meow, base_raster, field = "rlm_code")
 province_raster <- fasterize(eez_meow, base_raster, field = "pro_code")
-ecoregion_raster <- fasterize(eez_meow, base_raster, field = "eco_code")
-world_seas_raster <- fasterize(world_seas, base_raster, field = "mrgid")
 
 # Export rasters
 writeRaster(x = eez_raster,
@@ -40,14 +38,6 @@ writeRaster(x = realm_raster,
 
 writeRaster(x = province_raster,
             filename = file.path(project_path, "processed_data", "pro_raster.tif"),
-            overwrite = TRUE)
-
-writeRaster(x = ecoregion_raster,
-            filename = file.path(project_path, "processed_data", "eco_raster.tif"),
-            overwrite = TRUE)
-
-writeRaster(x = world_seas_raster,
-            filename = file.path(project_path, "processed_data", "world_seas_raster.tif"),
             overwrite = TRUE)
 
 # END OF SCRIPT #

### 2021-11-09 scripts/02_processing/06_get_costs_and_benefits.R

@@ -48,7 +48,8 @@ costs_raster <-
       "revenue_raster.tif"
     )
   ) %>% 
-  crop(benefits_raster)
+  crop(benefits_raster) %>% 
+  extend(benefits_raster)
 
 # Load spatial metadata rasters
 iso3n <-
@@ -61,13 +62,6 @@ rlm_code <-
 
 pro_code <-
   raster(file.path(project_path, "processed_data", "pro_raster.tif")) %>% 
-  crop(benefits_raster)
-
-eco_code <-
-  raster(file.path(project_path, "processed_data", "eco_raster.tif")) %>% 
-  crop(benefits_raster)
-
-seas_code <- raster(file.path(project_path, "processed_data", "world_seas_raster.tif")) %>% 
   crop(benefits_raster)
 
 # Load the EEZ vector data
@@ -90,16 +84,17 @@ world_seas <- st_read(file.path(
   rename(sea_name = name) %>% 
   as_tibble()
 
+area_raster <- raster::area(benefits_raster)
+
 ## PROCESSING ########################################################################
 # Extract codes for each pixel
 cb <-
   stack(iso3n,                   # Start by creating a raster stack of all features
         rlm_code,
         pro_code,
-        eco_code,
-        seas_code,
         benefits_raster,
-        costs_raster) %>%
+        costs_raster,
+        area_raster) %>%
   as.data.frame(xy = T) %>%       # Convert to data.frame, but keep coordinates
   rename(                         # Select and rename columns
     lon = x,
@@ -107,25 +102,22 @@ cb <-
     iso3n = eez_raster,
     rlm_code = rlm_raster,
     pro_code = pro_raster,
-    eco_code = eco_raster,
-    sea_code = world_seas_raster,
     benefit = suitability,
-    cost = revenue_raster
+    cost = revenue_raster,
+    area = layer
   ) %>%
   drop_na(iso3n, cost, benefit) %>%                             # Drop areas beyond national jurisdiction
   mutate(hemisphere = case_when(lon > 0 & lat > 0 ~ "NE",
                                 lon < 0 & lat > 0 ~ "NW",
                                 lon > 0 & lat <= 0 ~ "SE",
                                 lon < 0 & lat <= 0 ~ "SW"),
-         cost = pmax(cost, 0),
[…]

### 2021-11-09 scripts/03_descriptive_content/01_plot_supply_curves.R

@@ -12,7 +12,7 @@ library(cowplot)
 library(tidyverse)
 
 # Load data
-## National data
+## Global market
 ### By country
 eez_cb <- readRDS(
   file = file.path(project_path, "processed_data", "eez_costs_and_benefits.rds")
@@ -20,6 +20,17 @@ eez_cb <- readRDS(
 ### Horizontally summed
 eez_h_sum <- readRDS(
   file = file.path(project_path,"processed_data","eez_h_sum_costs_and_benefits.rds")
+)
+
+## Hemisphere market
+### By country-hemisphere
+hem_cb <- readRDS(
+  file = file.path(project_path, "processed_data", "hem_eez_costs_and_benefits.rds")
+)
+
+### Horizontally summed for each hemishpere
+hem_h_sum <- readRDS(
+  file = file.path(project_path,"processed_data","hem_h_sum_costs_and_benefits.rds")
 )
 
 ## Realm eez
@@ -42,15 +53,6 @@ pro_h_sum <- readRDS(
   file = file.path( project_path, "processed_data", "pro_h_sum_costs_and_benefits.rds")
 )
 
-#E Ecoregion eez
-## For each ecoregion, province, realm, and EEZ
-eco_eez_cb <- readRDS(
-  file = file.path( project_path, "processed_data", "eco_eez_costs_and_benefits.rds")
-)
-### Horizonbtaly summed for each ecoregion
-eco_eez_cb <- readRDS(
-  file = file.path( project_path, "processed_data", "eco_h_sum_costs_and_benefits.rds")
-)
 
 # PROCESSING ############################################################################################
 
@@ -72,6 +74,31 @@ eez <- ggplot(data = eez_cb,
        y = "Marginal Costs")
 
 eez_supply_curve <- plot_grid(eez, global, ncol = 2, labels = "AUTO")
+
+# Hemisphere
+
+eez_hem <- 
+  ggplot(data = hem_cb,
+         mapping = aes(x = tb, y = mc, group = iso3)) +
+  geom_line() +
+  guides(color = "none") +
+  scale_color_viridis_d() +
+  facet_wrap( ~ hemisphere, scales = "free") +
+  ggtheme_plot() +
+  labs(x = "Biodiversity",
+       y = "Marginal Costs")
+
+# Hem summed
+hem <- ggplot(data = hem_h_sum,
[…]

### 2021-11-09 scripts/03_descriptive_content/03_plot_global_benefits_and_costs.R

@@ -32,8 +32,7 @@ master_cb <- readRDS(
   file = file.path(project_path, "processed_data", "master_costs_and_benefits.rds")
 )
 
-coastline <- ne_countries(returnclass = "sf") %>% 
-  st_transform(epsg_moll)
+coastline <- ne_countries(returnclass = "sf")
 
 ## PLOT IT
 

### 2021-11-09 draft.Rmd

@@
 First, that habitat worth protecting is heterogeneously distributed across nations.
-And, secondly, that the costs of protecting habitat are non-perfectly correlated with the protection value of the pixel.
-Together, these two features make it possible to lower costs by using trade to protect the most cost-effective places.
-The magnitude of market gains (that is, cost savings relative to BAU unilateral conservation with no trade) will depend on the correlation between costs and benefits.
-To illustrate this point, we generate synthetic data to simulate 20 girded worlds where the conservation value of a pixel is heterogeneously distributed, and where costs and benefits exhibit varying degrees of correlation (R from -1 to 1; See methods for a detailed description on synthetic data generation).
+And, secondly, that the costs of protecting habitat are non-perfectly correlated with the protection value of the pixel and are thus also heterogeneous in space.
+Together, these two features make it possible to lower costs of conservation by using trade to protect the most cost-effective places.
+The magnitude of market gains (that is, cost savings relative to BAU unilateral conservation with no trade) will depend on the spatial distribution of costs and benefits.
+To illustrate this point, we generate synthetic data to simulate girded worlds where the conservation value of a pixel is heterogeneously distributed, and where costs and benefits exhibit different correlation coefficients (R from -1 to 1; See methods for a detailed description on synthetic data generation).
 For each scenario, we calculate the gains from trade for a series of protection targets (1 - 100%).
-We find that unless the costs and benefits are perfectly correlated (\emph{i.e.} R = 1), a market will always lower the costs of conservation for any desired target.
+We find that unless the costs and benefits are spatially homogeous and perfectly correlated (\emph{i.e.} R = 1), a market will always lower the costs of conservation for any desired target.
 
@@
 
-![\label{fig:rlm-map-of-trade}Map of trade for each realm.
+![\label{fig:rlm-map-of-trade}Map of trade for each Hemisphere.
 Blue indicates nations that reach the trading price before meeting their target, and therefore chose to pay to conerve elsewhere.
-Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/rlm_map_of_trade.png)
+Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/map_of_trade_hem.png)
 
@@
 
-![\label{fig:realms-per-eezs} Number of realms in each Exclusive Economic Zone](results/img/realms_per_eez.png)
-
 ![\label{fig:eezs-per-province} Number of Exclusive Economic Zones in each province](results/img/eezs_per_province.png)

### 2021-11-09 scripts/01_cleaning/06_create_hemisphere_raster.R
Hemisphere codes

@@ -41,9 +41,7 @@ hemispheres <- as.data.frame(base_raster, xy = T) %>%
     x > 0 & y < 0 ~ 4
   )) %>% 
   select(x, y, r) %>% 
-  rasterFromXYZ(crs = proj_moll)
-
-hemispheres_raster <- hemispheres * base_raster
+  rasterFromXYZ(crs = proj_longlat)
 
 hemispheres_raster_fn <- file.path(project_path, "processed_data", "hemispheres.tif")      # Define filename
 

### 2021-11-10 scripts/01_cleaning/08_clean_mpa_atlas.R
Added mpa cleaning script

@@ -1,0 +1,40 @@
+######################################################
+#title#
+######################################################
+#
+# Keep category Ia, Ib, and II. These are the only ones
+# that have a focus on ecosystem processes:
+# 
+# https://www.iucn.org/theme/protected-areas/about/protected-areas-categories/category-ii-national-park
+# 
+# Category Ia protected areas are strictly protected areas, generally with only limited human visitation. 
+# 
+# Category Ib and II protected areas are often similar in size and in their aim to protect functioning ecosystems.
+# 
+# Category III protected areas are generally centred on a particular natural feature, so that the primary focus of management is on maintaining this feature, whereas objectives of Ia are generally aimed at a whole ecosystem and ecosystem processes.
+# 
+# Category IV protected areas protect fragments of ecosystems or habitats, which often require continual management intervention to maintain.
+# 
+# Category V protected areas are generally cultural landscapes or seascapes that have been altered by humans over hundreds or even thousands of years and that rely on continuing intervention to maintain their qualities including biodiversity.
+# 
+# Category VI protected areas contain natural areas where biodiversity conservation is linked with sustainable use of natural resources, which is incompatible with category Ia. 
+#
+######################################################
+
+
+library(sf)
+library(janitor)
+library(tidyverse)
+
+mpas <-
+  st_read(
+    file.path(data_path, "mpa-atlas/mpatlas_20201223_clean"),
+    "mpatlas_20201223_clean"
+  ) %>%
+  clean_names(mpas) %>%
+  filter(iucn_categ %in% c("Ia", "Ib", "II"),
+         implemente == 1) %>%
+  select(mpa_id, wdpa_id, iso3 = sovereign)
+
+st_write(mpas,
+         file.path(project_path, "processed_data", "clean_mpa_atlas.gpkg"))

### 2021-11-10 scripts/02_processing/06_get_costs_and_benefits.R
REmoved usage of startR here

@@ -23,7 +23,6 @@
 
 ## SETUP #############################################################################
 # Load packages
-library(startR)
 library(raster)
 library(sf)
 library(tidyverse)

### 2021-11-10 scripts/02_processing/06_get_costs_and_benefits.R
Added hemisphere code raster to cost-benefit calculations

@@ -63,6 +63,11 @@ pro_code <-
   raster(file.path(project_path, "processed_data", "pro_raster.tif")) %>% 
   crop(benefits_raster)
 
+hem_code <- raster(file.path(project_path, "processed_data", "hemispheres.tif")) %>% 
+  crop(benefits_raster)
+
+area_raster <- raster::area(benefits_raster)
+
 # Load the EEZ vector data
 eez_meow <-
   st_read(file.path(
@@ -83,13 +88,13 @@ world_seas <- st_read(file.path(
   rename(sea_name = name) %>% 
   as_tibble()
 
-
 ## PROCESSING ########################################################################
 # Extract codes for each pixel
 cb <-
   stack(iso3n,                   # Start by creating a raster stack of all features
         rlm_code,
         pro_code,
+        hem_code,
         benefits_raster,
         costs_raster,
         area_raster) %>%
@@ -98,6 +103,7 @@ cb <-
     lon = x,
     lat = y,
     iso3n = eez_raster,
+    hem_code = hemispheres,
     rlm_code = rlm_raster,
     pro_code = pro_raster,
     benefit = suitability,

### 2021-11-10 scripts/02_processing/06_get_costs_and_benefits.R
Joning by hemisphere too

@@ -120,7 +120,7 @@ cb <-
 # Create a master dataset with all the metadata for each pixel
 master_data <- eez_meow %>%
   select(iso3, province, realm, iso3n, contains("code")) %>% 
-  left_join(cb, by = c("iso3n", "rlm_code", "pro_code")) %>%            # Join to the data.frame from rasters
+  left_join(cb, by = c("iso3n", "rlm_code", "pro_code", "hem_code")) %>%            # Join to the data.frame from rasters
   select(lon, lat, iso3, province, realm, hemisphere, benefit, cost) %>% # Select columns
   filter(benefit > 0) %>% 
   mutate(bcr = benefit / cost,                                                       # Calculate marginal benefit

### 2021-11-11 scripts/03_descriptive_content/04_mex_us_example_benefits_costs_bcr.R
re-ran figures

@@ -29,8 +29,7 @@ eez_cb <- readRDS(
   filter(!realm %in% c("Arctic", "Eastern Indo-Pacific"))
 
 coastline <- ne_countries(returnclass = "sf",scale = "large") %>% 
-  filter(iso_a3 %in% c("MEX", "USA")) %>% 
-  st_transform(epsg_moll)
+  filter(iso_a3 %in% c("MEX", "USA"))
 
 ## PLOT IT
 
@@ -46,8 +45,8 @@ benefit_map <- ggplot() +
   guides(fill = guide_colorbar(frame.colour = "black",
                                ticks.colour = "black")) +
   # theme(legend.position = "bottom") +
-  lims(y = c(1500000, 5900000),
-       x = c(-11900000, -5500000)) +
+  # lims(y = c(1500000, 5900000),
+       # x = c(-11900000, -5500000)) +
   ggtitle(label = "Habitat suitability is heterogeneously\ndistributed between and within nations",
           subtitle = "All pixels are 50 X 50 km")
 

### 2021-11-11 scripts/02_processing/04_intersect_eez_and_meow.R
Organizing fiure aand updating code

@@ -11,7 +11,6 @@
 
 ## Set up ##########################################################################################################
 # Load packages
-library(lwgeom)
 library(sf)
 library(tidyverse)
 
@@ -27,10 +26,10 @@ eez_meow <- eez %>%
   st_intersection(meow) %>% 
   select(iso3, iso3n,                                                 # Keep only relevant columns
          province, pro_code,
-         realm, rlm_code)
+         realm, rlm_code) 
 
 ## Export -----------------------------------------------------------------------------------------------------------
-intersected_eez_and_meow_fn <- file.path(project_path, "processed_data", "intersected_eez_meow_hem.gpkg") # File name
+intersected_eez_and_meow_fn <- file.path(project_path, "processed_data", "intersected_eez_and_meow.gpkg") # File name
 file.remove(intersected_eez_and_meow_fn)                                     # Remove any existing files
 st_write(obj = eez_meow, dsn = intersected_eez_and_meow_fn)                  # Write geopackage to disk
 

### 2021-11-11 scripts/02_processing/05_rasterize_eez_meow_seas.R

@@ -15,12 +15,8 @@ base_raster <-
   )
 
 # Load the vector data
-eez_meow <- st_read(file.path(project_path, "processed_data", "intersected_eez_meow_hem.gpkg")) %>% 
+eez_meow <- st_read(file.path(project_path, "processed_data", "intersected_eez_and_meow.gpkg")) %>% 
   select(iso3n, contains("code")) 
-
-# Load the vector data
-world_seas <- st_read(file.path(project_path, "processed_data", "clean_world_seas.gpkg"))
-
 
 # Rasterize
 eez_raster <- fasterize(eez_meow, base_raster, field = "iso3n")

### 2021-11-11 scripts/03_descriptive_content/01_plot_supply_curves.R

@@ -68,7 +68,7 @@ global <- ggplot(data = eez_h_sum,
 eez <- ggplot(data = eez_cb,
               mapping = aes(x = tb / 1e3, y = mc, group = iso3)) +
   geom_line() +
-  guides(color = F) +
+  guides(color = "none") +
   ggtheme_plot() +
   labs(x = bquote("Surface area (HS weighted; Thousand "~Km^2~")"),
        y = bquote("Fisheries revenue ($"~Km^-2~")"))
@@ -105,7 +105,7 @@ eez_rlm <-
   ggplot(data = rlm_eez_cb,
          mapping = aes(x = tb, y = mc, group = iso3)) +
   geom_line() +
-  guides(color = F) +
+  guides(color = "none") +
   scale_color_viridis_d() +
   facet_wrap( ~ realm, scales = "free") +
   ggtheme_plot() +
@@ -128,7 +128,7 @@ eez_pro <-
   ggplot(data = pro_h_sum,
          mapping = aes(x = tb, y = mc, color = iso3, group = paste(province, iso3))) +
   geom_line() +
-  guides(color = F) +
+  guides(color = "none") +
   scale_color_viridis_d() +
   facet_wrap( ~ realm, scales = "free") +
   ggtheme_plot() +
@@ -138,15 +138,22 @@ eez_pro <-
 
 # EXPORT PLOTS ##############################################################################################
 lazy_ggsave(plot = eez_supply_curve,
-            filename = "eez_supply_curve",
+            filename = "supply_curves/eez_supply_curve",
             width = 18, height = 7)
 
+lazy_ggsave(plot = eez_hem_supply_curve ,
+            filename = "supply_curves/eez_hem_supply_curve",
+            width = 20,
+            height = 20)
+
 lazy_ggsave(plot = eez_rlm_supply_curve ,
-            filename = "eez_rlm_supply_curve",
+            filename = "supply_curves/eez_rlm_supply_curve",
             width = 20,
             height = 20)
 
 lazy_ggsave(plot = eez_pro,
-            filename = "eez_pro_supply_curve")
+            filename = "supply_curves/eez_pro_supply_curve",
+            width = 20,
+            height = 20)
 
 # END OF SCRIPT

### 2021-11-11 scripts/03_descriptive_content/02_plot_trading_units.R

@@ -14,12 +14,11 @@ eez_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_costs_an
 rlm_eez_cb <- readRDS(file = file.path(project_path, "processed_data", "rlm_eez_costs_and_benefits.rds"))
 pro_eez_cb <- readRDS(file = file.path(project_path, "processed_data", "pro_eez_costs_and_benefits.rds"))
 
-eez_meow <- st_read(file.path(project_path, "processed_data", "intersected_eez_meow_hem.gpkg")) %>% 
-  ms_simplify()
+eez_meow <- st_read(file.path(project_path, "processed_data", "intersected_eez_and_meow.gpkg")) %>% 
+  ms_simplify(keep_shapes = T)
 
 # Load a coastline
-coast <- ne_countries(returnclass = "sf") %>% 
-  st_transform(crs = epsg_moll) 
+coast <- ne_countries(returnclass = "sf")
 
 # How many MEOWS per country?
 meows_per_eez <- eez_meow %>% 
@@ -27,8 +26,7 @@ meows_per_eez <- eez_meow %>%
   summarize(n_rlm = n_distinct(realm),
             n_pro = n_distinct(province)) %>% 
   ungroup() %>% 
-  arrange(desc(n_pro)) %>% 
-  ms_simplify(keep_shapes = TRUE)
+  arrange(desc(n_pro))
 
 rlm_per_eez <- ggplot() +
   geom_sf(data = coast) +

### 2021-11-11 scripts/03_descriptive_content/04_mex_us_example_benefits_costs_bcr.R

@@ -1,13 +1,13 @@
 ####################################################
-# Now that we have the targets and prices, we can 
+# Now that we have the targets and prices, we can
 # move forward and identify where biodiversity is
 # protected, and the associated costs of doing so.
-# 
+#
 # The benefits should be equivalent, since we are
 # using the same target.
 ####################################################
 
-# SET UP ################################################################################################
+# SET UP #######################################################################
 # Load packages
 library(startR)
 library(raster)
@@ -19,17 +19,20 @@ library(tidyverse)
 # Load data
 
 ## master data
-master_cb <- readRDS(file = file.path(project_path, "processed_data", "master_costs_and_benefits.rds")) %>% 
-  filter(iso3 %in% c("MEX", "USA")) %>% 
+master_cb <-
+  readRDS(file = file.path(
+    project_path,
+    "processed_data",
+    "master_costs_and_benefits.rds"
+  )) %>%
+  filter(iso3 %in% c("MEX", "USA")) %>%
   filter(!realm %in% c("Arctic", "Eastern Indo-Pacific"))
 
-eez_cb <- readRDS(
-  file = file.path(project_path, "processed_data", "eez_costs_and_benefits.rds")) %>% 
-  filter(iso3 %in% c("MEX", "USA")) %>% 
+eez_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_costs_and_benefits.rds")) %>%
+  filter(iso3 %in% c("MEX", "USA")) %>%
   filter(!realm %in% c("Arctic", "Eastern Indo-Pacific"))
 
-coastline <- ne_countries(returnclass = "sf",scale = "large") %>% 
-  filter(iso_a3 %in% c("MEX", "USA"))
+coastline <- ne_countries(country = c("Mexico", "United States of America"), returnclass = "sf", scale = 50) 
 
 ## PLOT IT
 
@@ -44,9 +47,8 @@ benefit_map <- ggplot() +
   scale_fill_viridis_c() +
   guides(fill = guide_colorbar(frame.colour = "black",
                                ticks.colour = "black")) +
-  # theme(legend.position = "bottom") +
-  # lims(y = c(1500000, 5900000),
-       # x = c(-11900000, -5500000)) +
+  lims(x = c(-135, -65),
+       y = c(10, 50)) +
   ggtitle(label = "Habitat suitability is heterogeneously\ndistributed between and within nations",
[…]

### 2021-11-11 scripts/02_processing/06_get_costs_and_benefits.R
Updated for PERC paper

@@ -73,19 +73,9 @@ eez_meow <-
   st_read(file.path(
     project_path,
     "processed_data",
-    "intersected_eez_meow_hem.gpkg"
+    "intersected_eez_and_meow.gpkg"
   )) %>% 
   st_drop_geometry() %>% 
-  as_tibble()
-
-# Load the world seas vectotr data
-world_seas <- st_read(file.path(
-  project_path,
-  "processed_data",
-  "clean_world_seas.gpkg"
-)) %>% 
-  st_drop_geometry() %>% 
-  rename(sea_name = name) %>% 
   as_tibble()
 
 ## PROCESSING ########################################################################
@@ -120,7 +110,7 @@ cb <-
 # Create a master dataset with all the metadata for each pixel
 master_data <- eez_meow %>%
   select(iso3, province, realm, iso3n, contains("code")) %>% 
-  left_join(cb, by = c("iso3n", "rlm_code", "pro_code", "hem_code")) %>%            # Join to the data.frame from rasters
+  left_join(cb, by = c("iso3n", "rlm_code", "pro_code")) %>%            # Join to the data.frame from rasters
   select(lon, lat, iso3, province, realm, hemisphere, benefit, cost) %>% # Select columns
   filter(benefit > 0) %>% 
   mutate(bcr = benefit / cost,                                                       # Calculate marginal benefit
@@ -228,30 +218,6 @@ pro_h_sum <- master_data %>%
   ) %>%
   ungroup()
 
-## AT THE SEALEVEL ####
-# Calculate country level and sea supply curve
-sea_eez <- master_data %>%
-  group_by(iso3, sea_name) %>%
-  arrange(desc(bcr)) %>%
-  mutate(
-    tb = cumsum(benefit),
-    tc = cumsum(cost),
-    pct = tb / sum(benefit),
-    pct_area = 1:n() / n()
-  ) %>%
-  ungroup()
-
-# Sum horizzontally for each realm
-sea_h_sum <- master_data %>%
-  group_by(sea_name) %>%
-  arrange(desc(bcr)) %>%
-  mutate(
-    tb = cumsum(benefit),
-    tc = cumsum(cost),
-    pct = tb / sum(benefit),
-    pct_area = 1:n() / n()
-  ) %>%
-  ungroup()
 
 ## DATA EXPORT ############################################################################
 # Export master data

### 2021-11-11 scripts/03_descriptive_content/02_plot_trading_units.R

@@ -1,3 +1,12 @@
+######################################################
+#title#
+######################################################
+# 
+# Purpose
+#
+######################################################
+
+## SET UP ######################################################################
 # Load packages
 library(startR)
 library(cowplot)
@@ -9,10 +18,10 @@ library(tidyverse)
 
 # Load data
 
-eez_h_sum_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_h_sum_costs_and_benefits.rds"))
-eez_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_costs_and_benefits.rds"))
-rlm_eez_cb <- readRDS(file = file.path(project_path, "processed_data", "rlm_eez_costs_and_benefits.rds"))
-pro_eez_cb <- readRDS(file = file.path(project_path, "processed_data", "pro_eez_costs_and_benefits.rds"))
+# eez_h_sum_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_h_sum_costs_and_benefits.rds"))
+# eez_cb <- readRDS(file = file.path(project_path, "processed_data", "eez_costs_and_benefits.rds"))
+# rlm_eez_cb <- readRDS(file = file.path(project_path, "processed_data", "rlm_eez_costs_and_benefits.rds"))
+# pro_eez_cb <- readRDS(file = file.path(project_path, "processed_data", "pro_eez_costs_and_benefits.rds"))
 
 eez_meow <- st_read(file.path(project_path, "processed_data", "intersected_eez_and_meow.gpkg")) %>% 
   ms_simplify(keep_shapes = T)
@@ -20,58 +29,18 @@ eez_meow <- st_read(file.path(project_path, "processed_data", "intersected_eez_a
 # Load a coastline
 coast <- ne_countries(returnclass = "sf")
 
-# How many MEOWS per country?
-meows_per_eez <- eez_meow %>% 
-  group_by(iso3) %>% 
-  summarize(n_rlm = n_distinct(realm),
-            n_pro = n_distinct(province)) %>% 
-  ungroup() %>% 
-  arrange(desc(n_pro))
 
-rlm_per_eez <- ggplot() +
-  geom_sf(data = coast) +
-  geom_sf(data = meows_per_eez, aes(fill = n_rlm)) +
-  scale_fill_viridis_c() +
-  ggtheme_map() +
-  labs(fill = "# of\nRealms") +
-  guides(fill = guide_colorbar(frame.colour = "black",
[…]

### 2021-11-11 scripts/03_descriptive_content/03_plot_global_benefits_and_costs.R

@@ -69,21 +69,21 @@ pannel <- plot_grid(benefit_map, cost_map, bcr_map,
 
 # Export figures
 lazy_ggsave(benefit_map,
-            "benefit_map",
+            "benefit_and_cost_maps/benefit_map",
             width = 15,
             height = 7)
 
 lazy_ggsave(cost_map,
-            "cost_map",
+            "benefit_and_cost_maps/cost_map",
             width = 15,
             height = 7)
 
 lazy_ggsave(bcr_map,
-            "bcr_map",
+            "benefit_and_cost_maps/bcr_map",
             width = 15,
             height = 7)
 
 lazy_ggsave(pannel,
-            "input_data_maps_panel",
+            "benefit_and_cost_maps/input_data_maps_panel",
             width = 15,
             height = 5)

### 2021-11-11 scripts/03_descriptive_content/04_mex_us_example_benefits_costs_bcr.R

@@ -41,7 +41,6 @@ coastline <- ne_countries(country = c("Mexico", "United States of America"), ret
 benefit_map <- ggplot() +
   geom_tile(data = master_cb, aes(x = lon, y = lat, fill = benefit / 2500)) +
   geom_sf(data = coastline, color = "black", size = 0.5) +
-  # coord_sf(crs = proj_longlat) +
   ggtheme_map() +
   labs(fill = bquote("Habitat\nsuitability")) +
   scale_fill_viridis_c() +
@@ -57,7 +56,6 @@ benefit_map <- ggplot() +
 cost_map <- ggplot() +
   geom_tile(data = master_cb, aes(x = lon, y = lat, fill = cost / 1e6)) +
   geom_sf(data = coastline, color = "black", size = 0.5) +
-  # coord_sf(crs = proj_longlat) +
   ggtheme_map() +
   labs(fill = bquote("Mean annual\nfisheries revenue\n(Million USD)")) +
   scale_fill_viridis_c() +
@@ -73,7 +71,6 @@ cost_map <- ggplot() +
 bcr_map <- ggplot() +
   geom_tile(data = master_cb, aes(x = lon, y = lat, fill = bcr)) +
   geom_sf(data = coastline, color = "black", size = 0.5) +
-  # coord_sf(crs = proj_longlat) +
   ggtheme_map() +
   labs(fill = bquote("Mean annual\nfisheries revenue\n(Million USD)")) +
   scale_fill_viridis_c(trans = "log10") +
@@ -87,20 +84,21 @@ bcr_map <- ggplot() +
 ggplot(eez_cb, aes(x = tb, y = mc, color = iso3)) +
   geom_line(size = 1) +
   ggtheme_plot() +
-  labs(x = "HS-weighted ")
+  labs(x = "HS-weighted ") +
+  scale_color_brewer(palette = "Set1")
 
 # Export figures
 lazy_ggsave(benefit_map,
-            "us_mex_benefit_map",
+            "benefit_and_cost_maps/us_mex_benefit_map",
             width = 15,
             height = 7)
 
 lazy_ggsave(cost_map,
-            "us_mex_cost_map",
+            "benefit_and_cost_maps/us_mex_cost_map",
             width = 15,
             height = 7)
 
 lazy_ggsave(bcr_map,
-            "us_mex_bcr_map",
+            "benefit_and_cost_maps/us_mex_bcr_map",
             width = 15,
             height = 7)

### 2021-11-11 scripts/04_analysis/03_get_eez_level_conservation.R

@@ -11,6 +11,7 @@
 # Load packages
 library(startR)
 library(cowplot)
+library(ggnewscale)
 library(rnaturalearth)
 library(sf)
 library(tidyverse)
@@ -34,7 +35,6 @@ trading_price <- eez_h_sum_cb %>%
 
 # Load a coastline
 coast <- ne_countries(returnclass = "sf") %>% 
-  st_transform(crs = epsg_moll) %>% 
   mutate(in_mkt = iso_a3 %in% unique(eez_cb$iso3))
 
 # Load EEZ geopackage
@@ -75,8 +75,7 @@ realized_bau_cb <- bau %>%
   group_by(approach, iso3) %>% 
   summarize(bau_tb = sum(benefit, na.rm = T),
             bau_tc = sum(cost, na.rm = T),
-            bau_mc = max(mc, na.rm = T),
-            bau_area = n() * 2500) %>% 
+            bau_mc = max(mc, na.rm = T)) %>% 
   ungroup()
 
 # For a market
@@ -84,8 +83,7 @@ realized_mkt_cb <- mkt %>%
   group_by(approach, iso3) %>% 
   summarize(mkt_tb = sum(benefit, na.rm = T),
             mkt_tc = sum(cost, na.rm = T),
-            mkt_mc = max(mc, na.rm = T),
-            mkt_area = n() * 2500) %>% 
+            mkt_mc = max(mc, na.rm = T)) %>% 
   ungroup()
 
 # Create a data.frame with the combined summarized outcomes
@@ -110,62 +108,27 @@ stops <- combined_outcomes %>%
   select(iso3, bau_mc) %>% 
   mutate(approach = "mkt")
 
-
-# gains_from_trade <- combined_outcomes %>% 
-#   select_if(is.numeric) %>% 
-#   select(-contains("stop")) %>% 
-#   summarize_all(sum, na.rm = T) %>% 
-#   gather(variable, value) %>% 
-#   separate(variable, into = c("approach", "variable")) %>% 
-#   spread(approach, value) %>% 
-#   mutate(difference = bau - mkt,
-#          ratio = mkt / bau)
-
-# got_paid <- combined_outcomes %>% 
-#   mutate(gets_paid = mc_stop <= trading_price,
-#          mkt_gains = bau_tc - mkt_tc) %>% 
-#   select(iso3, gets_paid, bau_tc, mkt_tc, mkt_gains) %>% 
[…]

### 2021-11-11 scripts/04_analysis/08_all_segments_all_scenarios.R

@@ -216,7 +216,7 @@ abs <- ggplot(gains_from_trade_multiple_scenarios, aes(x = r, y = difference, co
   ggtheme_plot() +
   labs(x = bquote("% Benefits ("~HS[i]*A[i]~")"), 
        y = "Costs avoided (BAU - MKT)",
-       color = "Segment") +
+       color = "Bubble policy") +
   scale_x_continuous(labels = scales::percent) +
   scale_color_brewer(palette = "Set1") +
   theme(legend.justification = c(0, 1),
@@ -238,8 +238,8 @@ gain_from_trade_segmented_market_plot <- plot_grid(abs, rel, ncol = 2, labels = 
 
 lazy_ggsave(plot = gain_from_trade_segmented_market_plot,
             file = "gain_from_trade_segmented_market_plot",
-            width = 20,
-            height = 7.5)
+            width = 25,
+            height = 10)
 
 write.csv(x = gains_from_trade_multiple_scenarios,
           file = file.path(project_path, "output_data", "gains_from_trade_bubbles.csv"),
